---
title: ClosED
output:
  html_document:
    theme: sandstone
    toc: false
    toc_float: false
    toc_depth: 5
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
##opts_chunk$set(dev = 'pdf')
opts_chunk$set(cache.path = 'cache/',
               width    = 200,
               fig.path = 'figures/',
               fig.height = 8,
               fig.width  = 8,
               warning     = FALSE,
               message     = FALSE,
               knitr.kable.NA = '')
options(knitr.kable.NA = '')

## Set a seed
set.seed(69027181)
```

# {.tabset .tabset-fade .tabset-pills}

Model  | Case Site    | Control Site         | Panel | Covariates
-------|--------------|----------------------|-------|----------------------------------------
0      | Individual   | None                 | ED    | closure
1      | Individual   | None                 | ED    | season + time + closure + nhs111 + other.centre + ambulance.diversion
2      | Individual   | Primary Matched      | ED    | season + time + closure + site +  closure * site + nhs111 + other.centre + ambulance.diversion
3      | All          | Primary Matched      | ED    | season + time + closure + site
4      | Individual   | None                 | LSOA  | season + time + change in ED time + nhs111 + other.centre + ambulance.diversion
5      | All          | None                 | LSOA  | season + time + change in ED time + site
6      | All          | None                 | LSOA  | season + time + change in ED time (Binary High/Low) + nhs111 + other.centre + ambulance.diversion

## Methods

```{r child = 'sections/methods.Rmd', eval = TRUE}
```

<!--- Run all analyses --->
```{r child = 'sections/analysis.Rmd', eval = TRUE}
```

## Results {.tabset .tabset-fadec .tabset-pills}
```{r child = 'sections/results.Rmd', eval = TRUE}
```

## References
