```{r load_data_again, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
load(file = '~/work/closed/nihr_report/data/results.RData')
## mutate(indicator = paste0(measure, ' ', sub.measure))
heatmap.coefficients <- closed_heatmap(df           = summary.models,
                                       site         = c('Bishop Auckland', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale'),
                                       colour.by    = 'coefficient',
                                       coef         = c('closure', 'diff.time.to.ed'),
                                       include.text = c('coefficient', 'se', 'p'),
                                       text.size    = 3,
                                       colour       = 'blue',
                                       final        = TRUE,
                                       digits       = 3)
heatmap.pvalues <- closed_heatmap(df           = summary.models,
                                  site         = c('Bishop Auckland', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale'),
                                  colour.by    = 'p',
                                  coef         = c('closure', 'diff.time.to.ed'),
                                  include.text = c('coefficient', 'se', 'p'),
                                  text.size    = 3,
                                  colour       = 'green',
                                  final        = TRUE,
                                  digits       = 3)
heatmap.standard <- closed_heatmap(df           = summary.models,
                                   site         = c('Bishop Auckland', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale'),
                                  colour.by    = 'standard',
                                  coef         = c('closure', 'diff.time.to.ed'),
                                  include.text = c('standard'),
                                  text.size    = 3.5,
                                  colour       = 'red',
                                  final        = TRUE,
                                  digits       = 3)

```

A lot of models and a lot of outcomes have been tested, to ease comprehension heatmaps showing the strength of association are shown below for the `closure` term in Site level models or the `difference in time to ED` for LSOA level models.  Three statistics have been used, the raw estimated coefficient (poor choice as outcomes vary, means, proportions or numbers), p-values (not the metric by which to initially judge effects) and standardised coefficients (`t` or `z` statistics depending on the model, these are preferred).  Its is to be expected that as you move across a given row there are similarities in the coefficients and as many of the indicators are themselves related they too will be correlated.

#### Bishop Auckland  {.tabset .tabset-fade .tabset-pills}

##### Standardised
```{r closed_heatmap_bishop_standard, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.standard$bishop

```

##### P-value
```{r closed_heatmap_bishop_pvalue, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.pvalues$bishop

```

##### Coefficient
```{r closed_heatmap_bishop_coefficient, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16, eval = TRUE}
heatmap.coefficients$bishop

```


#### Hartlepool {.tabset .tabset-fade .tabset-pills}


##### Standardised
```{r closed_heatmap_hartlepool_standard, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.standard$hartlepool

```

##### P-value
```{r closed_heatmap_hartlepool_pvalue, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.pvalues$hartlepool

```

##### Coefficient
```{r closed_heatmap_hartlepool_coefficient, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.coefficients$hartlepool

```

#### Hemel Hempstead {.tabset .tabset-fade .tabset-pills}

##### Standardised
```{r closed_heatmap_hemel_standard, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.standard$hemel

```

##### P-value
```{r closed_heatmap_hemel_pvalue, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.pvalues$hemel

```

##### Coefficient
```{r closed_heatmap_hemel_coefficient, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.coefficients$hemel

```

#### Newark {.tabset .tabset-fade .tabset-pills}

##### Standardised
```{r closed_heatmap_newark_standard, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.standard$newark

```

##### P-value
```{r closed_heatmap_newark_pvalue, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.pvalues$newark

```

##### Coefficient
```{r closed_heatmap_newark_coefficient, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.coefficients$newark

```

#### Rochdale {.tabset .tabset-fade .tabset-pills}


##### Standardised
```{r closed_heatmap_rochdale_standard, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.standard$rochdale

```

##### P-value
```{r closed_heatmap_rochdale_pvalue, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.pvalues$rochdale

```

##### Coefficient
```{r closed_heatmap_rochdale_coefficient, echo = FALSE, cache = FALSE, results = 'hide', fig.height = 20, fig.width = 16,  eval = TRUE}
heatmap.coefficients$rochdale

```
