##### Time-Series Plots

These time-series plots show the trends over time *before* the removal of any potentially spurious data points and the balancing of the panels.  They are presented for that very purpose, identification of possibly spurious data points.

###### Case Sites

```{r all_emergency_admissions_all_time_series_plot_case, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
names(emergency_admissions_site_measure) <- gsub("_", ".", names(emergency_admissions_site_measure))
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'all emergency admissions',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Bishop Auckland', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale'),
               legend        = TRUE)
```

###### Control Sites

```{r all_emergency_admissions_all_time_series_plot_control, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'all emergency admissions',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Salford', 'Scarborough', 'Whitehaven',
                                 'Blackburn', 'Grimsby', 'Wigan',
                                 'Basingstoke', 'Warwick', 'Yeovil',
                                 'Carlisle', 'Salisbury', 'Southport',
                                 'Rotherham', 'Scunthorpe', 'Wansbeck'),
               legend        = TRUE)
```

###### Bishop Auckland

```{r all_emergency_admissions_all_time_series_plot_bishop, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'all emergency admissions',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Bishop Auckland', 'Salford', 'Scarborough', 'Whitehaven'),
               legend        = TRUE)
```

###### Hartlepool

```{r all_emergency_admissions_all_time_series_plot_hartlepool, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'all emergency admissions',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

###### Hemel Hempstead

```{r all_emergency_admissions_all_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'all emergency admissions',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hemel Hempstead', 'Basingstoke', 'Warwick', 'Yeovil'),
               legend        = TRUE)
```

###### Newark

```{r all_emergency_admissions_all_time_series_plot_newark, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'all emergency admissions',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Newark', 'Carlisle', 'Salisbury', 'Southport'),
               legend        = TRUE)
```

###### Rochdale

```{r all_emergency_admissions_all_time_series_plot_rochdale, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'all emergency admissions',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Rochdale', 'Rotherham', 'Scunthorpe', 'Wansbeck'),
               legend        = TRUE)
```

##### Model 1
`Case Site    : Individual`\
`Control Site : None`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure + nhs111 + ambulance.divert + other.centre `\

```{r all_emergency_admissions_all_model1, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## all.emergency.admissions.all$model1.ts.plot
all.emergency.admissions.all$model1.forest$forest
all.emergency.admissions.all$model1.panelar.all$coef[3:8] %>% kable(caption = all.emergency.admissions.all$model1.panelar.all$caption)
```

##### Model 2

`Case Site    : Individual`\
`Control Site : One Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\

```{r all_emergency_admissions_all_model2, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
all.emergency.admissions.all$model2.ts.plot
all.emergency.admissions.all$model2.forest$forest
all.emergency.admissions.all$model2.panelar.all$coef[3:8] %>% kable(caption = all.emergency.admissions.all$model2.panelar.all$caption)
```

##### Model 3a

`Case Site    : Individual`\
`Control Site : All Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\

```{r all_emergency_admissions_all_model3a, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
all.emergency.admissions.all$model3a.ts.plot
all.emergency.admissions.all$model3a.forest$forest
all.emergency.admissions.all$model3a.panelar.all$coef[3:8] %>% kable(caption = all.emergency.admissions.all$model3a.panelar.all$caption)
```

##### Model 3b

`Case Site    : Individual and All`\
`Control Site : Pooled`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre`\

```{r all_emergency_admissions_all_model3b, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
all.emergency.admissions.all$model3b.ts.plot
all.emergency.admissions.all$model3b.forest$forest
all.emergency.admissions.all$model3b.panelar.all$coef[3:8] %>% kable(caption = all.emergency.admissions.all$model3b.panelar.all$caption)
```

##### Model 4

`Case Site    : All`\
`Control Site : One Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\

```{r all_emergency_admissions_all_model4, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
all.emergency.admissions.all$model4.ts.plot
all.emergency.admissions.all$model4.forest$forest
all.emergency.admissions.all$model4.panelar.all$coef[3:9] %>% kable(caption = all.emergency.admissions.all$model4.panelar.all$caption)
```

##### Model 5

`Case Site    : All`\
`Control Site : All Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\


```{r all_emergency_admissions_all_model5, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## all.emergency.admissions.all$model5.ts.plot
all.emergency.admissions.all$model5.forest$forest
all.emergency.admissions.all$model5.panelar.all$coef[3:9] %>% kable(caption = all.emergency.admissions.all$model5.panelar.all$caption)
```

##### Model 6

`Case Site    : Individual`\
`Control Site : One Matched`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre  + change in ED time`\

```{r all_emergency_admissions_all_model6, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
all.emergency.admissions.all$model6.ts.plot
all.emergency.admissions.all$model6.forest$forest
all.emergency.admissions.all$model6.panelar.all$coef[3:8] %>% kable(caption = all.emergency.admissions.all$model6.panelar.all$caption)
```

##### Model 7

`Case Site    : All`\
`Control Site : One Matched`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre  + change in ED time`\

```{r all_emergency_admissions_all_model7, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
all.emergency.admissions.all$model7.ts.plot
all.emergency.admissions.all$model7.forest$forest
all.emergency.admissions.all$model7.panelar.all$coef[3:8] %>% kable(caption = all.emergency.admissions.all$model7.panelar.all$caption)
```
