##### Time-Series Plots

These time-series plots show the trends over time *before* the removal of any potentially spurious data points and the balancing of the panels.  They are presented for that very purpose, identification of possibly spurious data points.

###### Case Sites

```{r avoidable_emergency_admissions_chest_time_series_plot_case, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'avoidable emergency admissions',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Bishop Auckland', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale'),
               legend        = TRUE)
```

###### Control Sites

```{r avoidable_emergency_admissions_chest_time_series_plot_control, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'avoidable emergency admissions',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Salford', 'Scarborough', 'Whitehaven',
                                 'Blackburn', 'Grimsby', 'Wigan',
                                 'Basingstoke', 'Warwick', 'Yeovil',
                                 'Carlisle', 'Salisbury', 'Southport',
                                 'Rotherham', 'Scunthorpe', 'Wansbeck'),
               legend        = TRUE)
```

###### Bishop Auckland

```{r avoidable_emergency_admissions_chest_time_series_plot_bishop, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'avoidable emergency admissions',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Bishop Auckland', 'Salford', 'Scarborough', 'Whitehaven'),
               legend        = TRUE)
kable(avoidable.emergency.admissions.chest$summary.table.bishop,
      align   = summary.table.align,
      caption = 'Pre and Post closure statistics and adjusted differences from the nine models tested in the Bishop Auckland cohort.')

```

###### Hartlepool

```{r avoidable_emergency_admissions_chest_time_series_plot_hartlepool, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'avoidable emergency admissions',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
kable(avoidable.emergency.admissions.chest$summary.table.bishop,
      align   = summary.table.align,
      caption = 'Pre and Post closure statistics and adjusted differences from the nine models tested in the Bishop Auckland cohort.')

```

###### Hemel Hempstead

```{r avoidable_emergency_admissions_chest_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'avoidable emergency admissions',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hemel Hempstead', 'Basingstoke', 'Warwick', 'Yeovil'),
               legend        = TRUE)
kable(avoidable.emergency.admissions.chest$summary.table.bishop,
      align   = summary.table.align,
      caption = 'Pre and Post closure statistics and adjusted differences from the nine models tested in the Bishop Auckland cohort.')

```

###### Newark

```{r avoidable_emergency_admissions_chest_time_series_plot_newark, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'avoidable emergency admissions',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Newark', 'Carlisle', 'Salisbury', 'Southport'),
               legend        = TRUE)
kable(avoidable.emergency.admissions.chest$summary.table.bishop,
      align   = summary.table.align,
      caption = 'Pre and Post closure statistics and adjusted differences from the nine models tested in the Bishop Auckland cohort.')

```

###### Rochdale

```{r avoidable_emergency_admissions_chest_time_series_plot_rochdale, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'avoidable emergency admissions',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Rochdale', 'Rotherham', 'Scunthorpe', 'Wansbeck'),
               legend        = TRUE)
kable(avoidable.emergency.admissions.chest$summary.table.bishop,
      align   = summary.table.align,
      caption = 'Pre and Post closure statistics and adjusted differences from the nine models tested in the Bishop Auckland cohort.')

```

##### Model 1
`Case Site    : Individual`\
`Control Site : None`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure + nhs111 + ambulance.divert + other.centre `\

```{r avoidable_emergency_admissions_chest_model1, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
avoidable.emergency.admissions.chest$model1.ts.plot
avoidable.emergency.admissions.chest$model1.forest$forest
avoidable.emergency.admissions.chest$model1.panelar.all$coef[3:8] %>% kable(caption = avoidable.emergency.admissions.chest$model1.panelar.all$caption)
```

##### Model 2

`Case Site    : Individual`\
`Control Site : Primary Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\

```{r avoidable_emergency_admissions_chest_model2, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
avoidable.emergency.admissions.chest$model2.ts.plot
avoidable.emergency.admissions.chest$model2.forest$forest
avoidable.emergency.admissions.chest$model2.panelar.all$coef[3:8] %>% kable(caption = avoidable.emergency.admissions.chest$model2.panelar.all$caption)
```

##### Model 3.1

`Case Site    : Individual`\
`Control Site : All Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\

```{r avoidable_emergency_admissions_chest_model3_1, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
avoidable.emergency.admissions.chest$model3.1.ts.plot
avoidable.emergency.admissions.chest$model3.1.forest$forest
avoidable.emergency.admissions.chest$model3.1.panelar.all$coef[3:8] %>% kable(caption = avoidable.emergency.admissions.chest$model3.1.panelar.all$caption)
```

##### Model 3.2

`Case Site    : Individual`\
`Control Site : All Matched (Pooled)`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre`\

```{r avoidable_emergency_admissions_chest_model3_2, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
avoidable.emergency.admissions.chest$model3.2.ts.plot
avoidable.emergency.admissions.chest$model3.2.forest$forest
avoidable.emergency.admissions.chest$model3.2.panelar.all$coef[3:8] %>% kable(caption = avoidable.emergency.admissions.chest$model3.2.panelar.all$caption)
```

##### Model 4

`Case Site    : All`\
`Control Site : Primary Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\

```{r avoidable_emergency_admissions_chest_model4, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
avoidable.emergency.admissions.chest$model4.ts.plot
avoidable.emergency.admissions.chest$model4.forest$forest
avoidable.emergency.admissions.chest$model4.panelar.all$coef[3:9] %>% kable(caption = avoidable.emergency.admissions.chest$model4.panelar.all$caption)
```

##### Model 5

`Case Site    : All`\
`Control Site : All Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\


```{r avoidable_emergency_admissions_chest_model5, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
avoidable.emergency.admissions.chest$model5.ts.plot
avoidable.emergency.admissions.chest$model5.forest$forest
avoidable.emergency.admissions.chest$model5.panelar.all$coef[3:9] %>% kable(caption = avoidable.emergency.admissions.chest$model5.panelar.all$caption)
```

##### Model 6.1

`Case Site    : Individual`\
`Control Site : None`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + nhs111 + ambulance.divert + other.centre  + change in ED time`\

```{r avoidable_emergency_admissions_chest_model6_1, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
avoidable.emergency.admissions.chest$model6.1.ts.plot
avoidable.emergency.admissions.chest$model6.1.forest$forest
avoidable.emergency.admissions.chest$model6.1.panelar.all$coef[3:8] %>% kable(caption = avoidable.emergency.admissions.chest$model6.1.panelar.all$caption)
```

##### Model 6.2

`Case Site    : Individual`\
`Control Site : Primary Matched`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + site + nhs111 + ambulance.divert + other.centre  + change in ED time`\

```{r avoidable_emergency_admissions_chest_model6_2, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
avoidable.emergency.admissions.chest$model6.2.ts.plot
avoidable.emergency.admissions.chest$model6.2.forest$forest
avoidable.emergency.admissions.chest$model6.2.panelar.all$coef[3:8] %>% kable(caption = avoidable.emergency.admissions.chest$model6.2.panelar.all$caption)
```


##### Model 7

`Case Site    : All`\
`Control Site : Primary Matched`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre  + change in ED time`\

```{r avoidable_emergency_admissions_chest_model7, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## avoidable.emergency.admissions.chest$model7.ts.plot
avoidable.emergency.admissions.chest$model7.forest$forest
avoidable.emergency.admissions.chest$model7.panelar.all$coef[3:8] %>% kable(caption = avoidable.emergency.admissions.chest$model7.panelar.all$caption)
```
