#### Model 1
`Case Site    : Individual`\
`Control Site : None`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure + nhs111 + ambulance.divert + other.centre `\

```{r critical_care_cips_all_model1, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
critical.care.cips.all$model1.ts.plot
critical.care.cips.all$model1.forest$forest
critical.care.cips.all$model1.panelar$coef[3:8] %>% kable(caption = critical.care.cips.all$model1.panelar$caption)
```

#### Model 2

`Case Site    : Individual`\
`Control Site : One Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\

```{r critical_care_cips_all_model2, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
critical.care.cips.all$model2.ts.plot
critical.care.cips.all$model2.forest$forest
critical.care.cips.all$model2.panelar$coef[3:8] %>% kable(caption = critical.care.cips.all$model2.panelar$caption)
```

#### Model 3

`Case Site    : Individual`\
`Control Site : All Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\

```{r critical_care_cips_all_model3, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
critical.care.cips.all$model3.ts.plot
critical.care.cips.all$model3.forest$forest
critical.care.cips.all$model3.panelar$coef[3:8] %>% kable(caption = critical.care.cips.all$model3.panelar$caption)
```

#### Model 4

`Case Site    : All`\
`Control Site : One Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\

```{r critical_care_cips_all_model4, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
critical.care.cips.all$model4.ts.plot.trust
critical.care.cips.all$model4.forest$forest
critical.care.cips.all$model4.panelar$coef[3:9] %>% kable(caption = critical.care.cips.all$model4.panelar$caption)
## critical.care.cips.all$model4.ts.plot.lsoa
```

#### Model 5

`Case Site    : All`\
`Control Site : All Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre `\


```{r critical_care_cips_all_model5, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
critical.care.cips.all$model5.ts.plot.trust
critical.care.cips.all$model5.forest$forest
critical.care.cips.all$model5.panelar$coef[3:9] %>% kable(caption = critical.care.cips.all$model5.panelar$caption)
```

#### Model 6

`Case Site    : Individual`\
`Control Site : One Matched`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre  + change in ED time`\

```{r critical_care_cips_all_model6, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
critical.care.cips.all$model6.ts.plot.trust
critical.care.cips.all$model6.forest.model$forest
critical.care.cips.all$model6.panelar$coef[3:8] %>% kable(caption = critical.care.cips.all$model6.panelar$caption)
```

#### Model 7

Model 7 seeks to analyse at the LSOA level across all case sites and their one matched contorl site the effects of the various steps, and other co-variates.  However, the amount of RAM required by the software is (~26Gb if only one matched control site, rising to 126Gb if all contorl sites are included as there are 2648 LSOAs) exceeds the 16Gb available on the Virtual Machine.

`Case Site    : All`\
`Control Site : One Matched`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre  + change in ED time`\

```{r critical_care_cips_all_model7, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
critical.care.cips.all$model7.ts.plot.trust
critical.care.cips.all$model7.forest.model$forest
critical.care.cips.all$model7.panelar$coef[3:8] %>% kable(caption = critical.care.cips.all$model7.panelar$caption)
```
