### ED Attendance by Mode of Arrival - Any {.tabset .tabset-fade .tabset-pills}

#### Model 1
```{r mode_or_arrival_model1, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
mode.of.arrival.any$model1.ts.plot
kable(mode.of.arrival.any$model1.forest$summary)
```
#### Model 2
```{r mode_or_arrival_model2, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
mode.of.arrival.any$model2.ts.plot
kable(mode.of.arrival.any$model2.forest$summary)
```
#### Model 3
```{r mode_or_arrival_model3, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
mode.of.arrival.any$model3.ts.plot
kable(mode.of.arrival.any$model3.forest$summary)
```

#### Model 4

Model 4 seeks to analyse at the LSOA level across all sites (cases and all controls) the effects of the various steps, and other co-variates.  However, there are 2648 LSOAs (i.e panels) and the amount of RAM required by the software is 120Gb which currently exceeds the 16Gb available on the Virtual Machine.

```{r mode_or_arrival_model4, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
mode.of.arrival.any$model4.ts.plot.trust
kable(mode.of.arrival.any$model4.forest$summary)
```

#### Model 5

```{r mode_or_arrival_model4, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
mode.of.arrival.any$model4.ts.plot.trust
kable(mode.of.arrival.any$model4.forest$summary)
```
