#### Model 1
`Case Site    : Individual`
`Control Site : None`
`Panel        : ED`
`Model        : observations ~ season + time + closure + steps`

```{r mode_of_arrival_any_model1, echo = FALSE, cache = FALSE, results = 'markup', fig.height = 8, fig.width = 8, eval	= TRUE}
mode.of.arrival.any$model1.ts.plot
mode.of.arrival.any$model1.forest$forest
mode.of.arrival.any$model1.panelar[3:8] %>% kable()
```

#### Model 2

`Case Site    : Individual`
`Control Site : One Matched with Steps`
`Panel        : ED`
`Model        : observations ~ season + time + closure * site + steps`

```{r mode_of_arrival_any_model2, echo = FALSE, cache = FALSE, results = 'markup', fig.height = 8, fig.width = 8, eval = TRUE}
mode.of.arrival.any$model2.ts.plot
mode.of.arrival.any$model2.forest$forest
mode.of.arrival.any$model2.panelar[3:8] %>% kable()
```

#### Model 3

`Case Site    : Individual`
`Control Site : One Matched with Steps`
`Panel        : LSOA`
`Model        : observations ~ season + time + closure * site + steps + change in ED time`

```{r mode_of_arrival_any_model3, echo = FALSE, cache = FALSE, results = 'markup', fig.height = 8, fig.width = 8, eval = TRUE}
mode.of.arrival.any$model3.ts.plot.trust
mode.of.arrival.any$model3.forest$forest
mode.of.arrival.any$model3.panelar[3:8] %>% kable()
## mode.of.arrival.any$model3.ts.plot.lsoa
```

#### Model 4

`Case Site    : All`
`Control Site : All`
`Panel        : LSOA`
`Model        : observations ~ season + time + closure * site + steps + change in ED time`

Model 4 seeks to analyse at the LSOA level across all sites (cases and all controls) the effects of the various steps, and other co-variates.  However, there are 2648 LSOAs (i.e panels) and the amount of RAM required by the software is 120Gb which currently exceeds the 16Gb available on the Virtual Machine.

```{r mode_or_arrival_any_model4, echo = FALSE, cache = FALSE, results = 'markup', fig.height = 8, fig.width = 8, eval = TRUE}
mode.of.arrival.any$model4.ts.plot.trust
## mode.of.arrival.any$model4.forest$forest
## mode.of.arrival.any$model4.panelar[3:8]
```

#### Model 5

`Case Site    : All`
`Control Site : All`
`Panel        : LSOA`
`Model        : observations ~ season + time + closure * site + steps`

```{r mode_or_arrival_any_model5, echo = FALSE, cache = FALSE, results = 'markup', fig.height = 8, fig.width = 8, eval = TRUE}
mode.of.arrival.any$model4.ts.plot.trust
## mode.of.arrival.any$model4.forest$forest
## mode.of.arrival.any$model5.panelar[3:8]
```
