## ED Attendance by Mode of Arrival (Pooled Control)

### Bishop Auckland General Hospital

#### Any

```{r bishop_attendance_any_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
bishop.attendance.any.pooled$ts.plot.events
```
```{r bishop_attendance_any_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
bishop.attendance.any.pooled$panelar %>% summary()
```

#### Ambulance

```{r bishop_attendance_ambulance_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
bishop.attendance.ambulance.pooled$ts.plot.events
```
```{r bishop_attendance_ambulance_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
bishop.attendance.ambulance.pooled$panelar %>% summary()
```

#### Other

```{r bishop_attendance_other_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
bishop.attendance.other.pooled$ts.plot.events
```
```{r bishop_attendance_other_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
bishop.attendance.other.pooled$panelar %>% summary()
```

### Hemel Hempstead Hospital

#### Any

```{r hemel_attendance_any_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hemel.attendance.any.pooled$ts.plot.events
```
```{r hemel_attendance_any_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hemel.attendance.any.pooled$panelar %>% summary()
```

#### Ambulance

```{r hemel_attendance_ambulance_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hemel.attendance.ambulance.pooled$ts.plot.events
```
```{r hemel_attendance_ambulance_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hemel.attendance.ambulance.pooled$panelar %>% summary()
```

#### Other

```{r hemel_attendance_other_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hemel.attendance.other.pooled$ts.plot.events
```
```{r hemel_attendance_other_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hemel.attendance.other.pooled$panelar %>% summary()
```

### Newark Hospital

#### Any

```{r newark_attendance_any_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
newark.attendance.any.pooled$ts.plot.events
```
```{r newark_attendance_any_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
newark.attendance.any.pooled$panelar %>% summary()
```

#### Ambulance

```{r newark_attendance_ambulance_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
newark.attendance.ambulance.pooled$ts.plot.events
```
```{r newark_attendance_ambulance_pooled_panel, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
newark.attendance.ambulance.pooled$panelar %>% summary()
```
#### Other

```{r newark_attendance_other_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
newark.attendance.other.pooled$ts.plot.events
```
```{r newark_attendance_other_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
newark.attendance.other.pooled$panelar %>% summary()
```

### Rochdale Infirmary

#### Any
```{r rochdale_attendance_any_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
rochdale.attendance.any.pooled$ts.plot.events
```
```{r rochdale_attendance_any_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
rochdale.attendance.any.pooled$panelar %>% summary()

#### Ambulance
```{r rochdale_attendance_ambulance_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
rochdale.attendance.ambulance.pooled$ts.plot.events
```
```{r rochdale_attendance_ambulance_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
rochdale.attendance.ambulance.pooled$panelar %>% summary()

#### Other
```{r rochdale_attendance_other_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
rochdale.attendance.other.pooled$ts.plot.events
```
```{r rochdale_attendance_other_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
rochdale.attendance.other.pooled$panelar %>% summary()
```

### University Hospital of Hartlepool

#### Any
```{r hartlepool_attendance_any_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hartlepool.attendance.any.pooled$ts.plot.events
```
```{r hartlepool_attendance_any_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hartlepool.attendance.any.pooled$panelar %>% summary()
```

#### Ambulance
```{r hartlepool_attendance_ambulance_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hartlepool.attendance.ambulance.pooled$ts.plot.events
```
```{r hartlepool_attendance_ambulance_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hartlepool.attendance.ambulance.pooled$panelar %>% summary()
```

#### Other
```{r hartlepool_attendance_other_pooled_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hartlepool.attendance.other.pooled$ts.plot.events
```
```{r hartlepool_attendance_other_pooled_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hartlepool.attendance.other.pooled$panelar %>% summary()
```


```{r echo = FALSE, cache = FALSE, eval = TRUE}
rm(ed_attendances_by_mode_measure.pooled,
   bishop.attendance.any.pooled,
   bishop.attendance.ambulance.pooled,
   bishop.attendance.other.pooled,
   hemel.attendance.any.pooled,
   hemel.attendance.ambulance.pooled,
   hemel.attendance.other.pooled,
   newark.attendance.any.pooled,
   newark.attendance.ambulance.pooled,
   newark.attendance.other.pooled,
   rochdale.attendance.any.pooled,
   rochdale.attendance.ambulance.pooled,
   rochdale.attendance.other.pooled,
   hartlepool.attendance.any.pooled,
   hartlepool.attendance.ambulance.pooled,
   hartlepool.attendance.other.pooled)
```
