### ED Attendance by Mode of Arrival  {.tabset .tabset-fade .tabset-pills}

#### Bishop Auckland General Hospital

##### Any
```{r bishop_attendance_any_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
bishop.attendance.any.matched$ts.plot.events
```
```{r bishop_attendance_any_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
bishop.attendance.any.matched$panelar %>% summary()
```

##### Ambulance
```{r bishop_attendance_ambulance_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
bishop.attendance.ambulance.matched$ts.plot.events
```
```{r bishop_attendance_ambulance_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
bishop.attendance.ambulance.matched$panelar %>% summary()
```

##### Other
```{r bishop_attendance_other_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
bishop.attendance.other.matched$ts.plot.events
```
```{r bishop_attendance_other_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
bishop.attendance.other.matched$panelar %>% summary()
```

#### Hemel Hempstead Hospital

##### Any
```{r hemel_attendance_any_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hemel.attendance.any.matched$ts.plot.events
```
```{r hemel_attendance_any_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hemel.attendance.any.matched$panelar %>% summary()
```

##### Ambulance
```{r hemel_attendance_ambulance_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hemel.attendance.ambulance.matched$ts.plot.events
```
```{r hemel_attendance_ambulance_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hemel.attendance.ambulance.matched$panelar %>% summary()
```

##### Other
```{r hemel_attendance_other_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hemel.attendance.other.matched$ts.plot.events
```
```{r hemel_attendance_other_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hemel.attendance.other.matched$panelar %>% summary()
```

#### Newark Hospital

##### Any
```{r newark_attendance_any_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
newark.attendance.any.matched$ts.plot.events
```
```{r newark_attendance_any_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
newark.attendance.any.matched$panelar %>% summary()
```

##### Ambulance
```{r newark_attendance_ambulance_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
newark.attendance.ambulance.matched$ts.plot.events
```
```{r newark_attendance_ambulance_matched_panel, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
newark.attendance.ambulance.matched$panelar %>% summary()
```
##### Other
```{r newark_attendance_other_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
newark.attendance.other.matched$ts.plot.events
```
```{r newark_attendance_other_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
newark.attendance.other.matched$panelar %>% summary()
```

#### Rochdale Infirmary

##### Any
```{r rochdale_attendance_any_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
rochdale.attendance.any.matched$ts.plot.events
```
```{r rochdale_attendance_any_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
rochdale.attendance.any.matched$panelar %>% summary()
```

##### Ambulance
```{r rochdale_attendance_ambulance_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
rochdale.attendance.ambulance.matched$ts.plot.events
```
```{r rochdale_attendance_ambulance_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
rochdale.attendance.ambulance.matched$panelar %>% summary()
```

##### Other
```{r rochdale_attendance_other_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
rochdale.attendance.other.matched$ts.plot.events
```
```{r rochdale_attendance_other_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
rochdale.attendance.other.matched$panelar %>% summary()
```

#### University Hospital of Hartlepool

##### Any
```{r hartlepool_attendance_any_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hartlepool.attendance.any.matched$ts.plot.events
```
```{r hartlepool_attendance_any_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hartlepool.attendance.any.matched$panelar %>% summary()
```

##### Ambulance
```{r hartlepool_attendance_ambulance_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hartlepool.attendance.ambulance.matched$ts.plot.events
```
```{r hartlepool_attendance_ambulance_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hartlepool.attendance.ambulance.matched$panelar %>% summary()
```

##### Other
```{r hartlepool_attendance_other_matched_plot, echo = FALSE, cache = FALSE, results = 'asis', eval = TRUE}
hartlepool.attendance.other.matched$ts.plot.events
```
```{r hartlepool_attendance_other_matched_panelar, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
hartlepool.attendance.other.matched$panelar %>% summary()
```

#### Summary

##### Any Attendance
```{r summary_attendance_any_matched, echo = FALSE, cache = FALSE, eval = TRUE}
summary.attendance.any.matched <- closed_forest(df.list   = list(bishop.attendance.any.matched$coefficients,
                                                                 hartlepool.attendance.any.matched$coefficients,
                                                                 hemel.attendance.any.matched$coefficients,
                                                                 newark.attendance.any.matched$coefficients,
                                                                 rochdale.attendance.any.matched$coefficients),
                                                plot.term = c('time.to.ed', 'closure'),
                                                title     = 'ED Attendance (Any) v Matched Control',
                                               digits    = 3)
kable(summary.attendance.any.matched$summary)
summary.attendance.any.matched$forest```
```

##### Ambulance Attendance
```{r summary_attendance_ambulance_matched, echo = FALSE, cache = FALSE, eval = TRUE}
summary.attendance.ambulance.matched <- closed_forest(df.list   = list(bishop.attendance.ambulance.matched$coefficients,
                                                                 hartlepool.attendance.ambulance.matched$coefficients,
                                                                 hemel.attendance.ambulance.matched$coefficients,
                                                                 newark.attendance.ambulance.matched$coefficients,
                                                                 rochdale.attendance.ambulance.matched$coefficients),
                                                plot.term = c('time.to.ed', 'closure'),
                                                title     = 'ED Attendance (Ambulance) v Matched Control',
                                                digits    = 3)
kable(summary.attendance.ambulance.matched$summary)
summary.attendance.ambulance.matched$forest
```

##### Other Attendance
```{r summary_attendance_other_matched, echo = FALSE, cache = FALSE, eval = TRUE}
summary.attendance.other.matched <- closed_forest(df.list   = list(bishop.attendance.other.matched$coefficients,
                                                                 hartlepool.attendance.other.matched$coefficients,
                                                                 hemel.attendance.other.matched$coefficients,
                                                                 newark.attendance.other.matched$coefficients,
                                                                 rochdale.attendance.other.matched$coefficients),
                                                plot.term = c('time.to.ed', 'closure'),
                                                title     = 'ED Attendance (Other) v Matched Control',
                                                digits    = 3)
kable(summary.attendance.other.matched$summary)
summary.attendance.other.matched$forest
```

```{r echo = FALSE, cache = FALSE, eval = TRUE}
rm(ed_attendances_by_mode_measure.matched,
   bishop.attendance.any.matched,
   bishop.attendance.ambulance.matched,
   bishop.attendance.other.matched,
   hemel.attendance.any.matched,
   hemel.attendance.ambulance.matched,
   hemel.attendance.other.matched,
   newark.attendance.any.matched,
   newark.attendance.ambulance.matched,
   newark.attendance.other.matched,
   rochdale.attendance.any.matched,
   rochdale.attendance.ambulance.matched,
   rochdale.attendance.other.matched,
   hartlepool.attendance.any.matched,
   hartlepool.attendance.ambulance.matched,
   hartlepool.attendance.other.matched)
```
