##### Time-Series Plots

These time-series plots show the trends over time *before* the removal of any potentially spurious data points and the balancing of the panels.  They are presented for that very purpose, identification of possibly spurious data points.

<!-- ###### Case Sites -->

<!-- ```{r template.time.series.plot.case, echo = FALSE, cache = FALSE, results = 'hide' eval = TRUE} -->
<!-- closed_ts_plot(df            = df_site_measure_clean, -->
<!--                indicator     = 'measure', -->
<!--                sub.indicator = 'submeasure', -->
<!--                steps         = TRUE, -->
<!--                theme         = theme_bw(), -->
<!--                tidy          = FALSE, -->
<!--                facet         = FALSE, -->
<!--                sites         = c('Bishop Auckland', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale'), -->
<!--                legend        = TRUE) -->
<!-- ``` -->

<!-- ###### Control Sites -->

<!-- ```{r template.time.series.plot.control, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE} -->
<!-- closed_ts_plot(df            = df_site_measure_clean, -->
<!--                indicator     = 'measure', -->
<!--                sub.indicator = 'submeasure', -->
<!--                steps         = TRUE, -->
<!--                theme         = theme_bw(), -->
<!--                tidy          = FALSE, -->
<!--                facet         = FALSE, -->
<!--                sites         = c('Salford', 'Scarborough', 'Whitehaven', -->
<!--                                  'Blackburn', 'Grimsby', 'Wigan', -->
<!--                                  'Basingstoke', 'Warwick', 'Yeovil', -->
<!--                                  'Carlisle', 'Salisbury', 'Southport', -->
<!--                                  'Rotherham', 'Scunthorpe', 'Wansbeck'), -->
<!--                legend        = TRUE) -->
<!-- ``` -->

##### Bishop Auckland
```{r template.bishop.plot, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = data_frame_site_measure_clean,
               indicator     = 'Measure',
               sub.indicator = 'sub_measure',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Bishop Auckland', 'Salford', 'Scarborough', 'Whitehaven'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = FALSE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
kable(template$summary.table.bishop,
      align   = summary.table.align,
      format   = 'pandoc',
      caption = 'Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Bishop Auckland cohort.')
## print('Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Bishop Auckland cohort.')
## pander(template$summary.table.bishop)

```


##### Hartlepool
```{r template.hartlepool.plot, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = data_frame_site_measure_clean,
               indicator     = 'Measure',
               sub.indicator = 'sub_measure',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = FALSE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
kable(template$summary.table.hartlepool,
      align   = summary.table.align,
      format   = 'pandoc',
      caption = 'Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Hartlepool cohort.')
## print('Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Hartlepool cohort.')
## pander(template$summary.table.hartlepool)

```

##### Hemel Hempstead
```{r template.hemel.plot, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = data_frame_site_measure_clean,
               indicator     = 'Measure',
               sub.indicator = 'sub_measure',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Hemel Hempstead', 'Basingstoke', 'Warwick', 'Yeovil'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = FALSE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
kable(template$summary.table.hemel,
      align   = summary.table.align,
      format   = 'pandoc',
      caption = 'Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Hemel Hempstead cohort.')
## print('Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Hemel Hempstead cohort.')
## pander(template$summary.table.hemel)

```

##### Newark
```{r template.newark.plot, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = data_frame_site_measure_clean,
               indicator     = 'Measure',
               sub.indicator = 'sub_measure',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Newark', 'Carlisle', 'Salisbury', 'Southport'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = FALSE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
kable(template$summary.table.newark,
      align   = summary.table.align,
      format   = 'pandoc',
      caption = 'Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Newark cohort.')
## print('Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Newark cohort.')
## pander(template$summary.table.newark)

```

##### Rochdale
```{r template.rochdale.plot, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = data_frame_site_measure_clean,
               indicator     = 'Measure',
               sub.indicator = 'sub_measure',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Rochdale', 'Rotherham', 'Scunthorpe', 'Wansbeck'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = FALSE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
kable(template$summary.table.rochdale,
      align   = summary.table.align,
      format   = 'pandoc',
      caption = 'Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Rochdale cohort.')
## print('Pre and Post closure statistics and adjusted differences in DESCRIPTION from the nine models tested in the Rochdale cohort.')
## pander(template$summary.table.rochdale)

```

##### Model 1
`Case Site    : Individual`\
`Control Site : None`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure + nhs111 + ambulance.divert + other.centre`\

```{r template.model1, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## template$model1.ts.plot
## Set variables
measure <- 'Measure'
sub.measure <- 'sub_measure'
## Set sites to plot
sites <- c('Bishop Auckland', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale')
## Filter
to.plot <- filter(ed_attendances_by_mode_site_measure_clean,
                  town %in% sites &
                  measure == measure,
                  sub.measure == sub.measure)
## Plot
closed_ts_plot(df            = to.plot,
               sites         = sites,
               indicator     = measure,
               sub.indicator = sub.measure,
               steps         = TRUE,
               lines         = TRUE,
               xaxis.steps   = FALSE,
               join.line     = TRUE,
               legend        = FALSE,
               facet         = FALSE)
template$model1.forest$forest
template$model1.panelar.all$coef[3:8] %>% kable(caption = template$model1.panelar.all$caption)
```

##### Model 2

`Case Site    : Individual`\
`Control Site : Primary Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre`\

```{r template.model2, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## template$model2.ts.plot
## Set sites to plot
sites <- c('Bishop Auckland', 'Whitehaven',
                   'Hartlepool', 'Grimsby',
                   'Hemel Hempstead', 'Warwick',
                   'Newark', 'Southport',
                   'Rochdale', 'Rotherham')
## Filter
to.plot <- filter(ed_attendances_by_mode_site_measure_clean,
                  town %in% sites &
                  measure == measure,
                  sub.measure == sub.measure)
## Plot
closed_ts_plot(df            = to.plot,
               sites         = sites,
               indicator     = measure,
               sub.indicator = sub.measure,
               steps         = TRUE,
               lines         = TRUE,
               xaxis.steps   = FALSE,
               join.line     = TRUE,
               legend        = TRUE,
               facet         = TRUE)
template$model2.forest$forest
template$model2.panelar.all$coef[3:8] %>% kable(caption = template$model2.panelar.all$caption)
```

##### Model 3.1

`Case Site    : Individual`\
`Control Site : All Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre`\

```{r template.model3_1, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## template$model3.1.ts.plot
## Set sites to plot
sites <- c('Basingstoke', 'Bishop Auckland', 'Blackburn', 'Carlisle', 'Grimsby', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale', 'Rotherham', 'Salford', 'Salisbury', 'Scarborough', 'Scunthorpe', 'Southport', 'Wansbeck', 'Warwick', 'Whitehaven', 'Wigan', 'Yeovil')
## Filter
to.plot <- filter(ed_attendances_by_mode_site_measure_clean,
                  town %in% sites &
                  measure == measure,
                  sub.measure == sub.measure)
## Plot
closed_ts_plot(df            = to.plot,
               sites         = sites,
               indicator     = measure,
               sub.indicator = sub.measure,
               steps         = TRUE,
               lines         = TRUE,
               xaxis.steps   = FALSE,
               join.line     = TRUE,
               legend        = TRUE,
               facet         = TRUE)
template$model3.1.forest$forest
template$model3.1.panelar.all$coef[3:8] %>% kable(caption = template$model3.1.panelar.all$caption)
```

##### Model 3.2

`Case Site    : Individual`\
`Control Site : All Matched (Pooled)`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre`\

```{r template.model3_2, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## template$model3.2.ts.plot
## Set sites to plot
sites <- c('Bishop Auckland', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale', 'Control')
## Filter
to.plot <- closed_pool(df = ed_attendances_by_mode_site_measure,
                       within.centres = TRUE) # %>% closed_clean()
## Plot
closed_ts_plot(df            = to.plot,
               sites         = sites,
               indicator     = measure,
               sub.indicator = sub.measure,
               steps         = TRUE,
               lines         = TRUE,
               xaxis.steps   = FALSE,
               join.line     = TRUE,
               legend        = TRUE,
               facet         = TRUE)
template$model3.2.forest$forest
template$model3.2.panelar.all$coef[3:8] %>% kable(caption = template$model3.2.panelar.all$caption)
```

##### Model 4

`Case Site    : All`\
`Control Site : Primary Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre`\

```{r template.model4, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## template$model4.ts.plot
sites <- c('Bishop Auckland', 'Whitehaven',
           'Hartlepool', 'Grimsby',
           'Hemel Hempstead', 'Warwick',
           'Newark', 'Southport',
           'Rochdale', 'Rotherham')
## Filter
to.plot <- filter(ed_attendances_by_mode_site_measure_clean,
                  town %in% sites &
                  measure == measure,
                  sub.measure == sub.measure)
## Plot
closed_ts_plot(df            = to.plot,
               sites         = sites,
               indicator     = measure,
               sub.indicator = sub.measure,
               steps         = TRUE,
               lines         = TRUE,
               xaxis.steps   = FALSE,
               join.line     = TRUE,
               legend        = TRUE,
               facet         = TRUE)
template$model4.forest$forest
template$model4.panelar.all$coef[3:9] %>% kable(caption = template$model4.panelar.all$caption)
```

##### Model 5

`Case Site    : All`\
`Control Site : All Matched`\
`Panel        : ED`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre`\


```{r template.model5, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## template$model5.ts.plot
## Model 5
sites <- c('Basingstoke', 'Bishop Auckland', 'Blackburn', 'Carlisle', 'Grimsby', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale', 'Rotherham', 'Salford', 'Salisbury', 'Scarborough', 'Scunthorpe', 'Southport', 'Wansbeck', 'Warwick', 'Whitehaven', 'Wigan', 'Yeovil')
## Filter
to.plot <- filter(ed_attendances_by_mode_site_measure_clean,
                  town %in% sites &
                  measure == measure,
                  sub.measure == sub.measure)
## Plot
closed_ts_plot(df            = to.plot,
               sites         = sites,
               indicator     = measure,
               sub.indicator = sub.measure,
               steps         = TRUE,
               lines         = TRUE,
               xaxis.steps   = FALSE,
               join.line     = TRUE,
               legend        = TRUE,
               facet         = TRUE)
template$model5.forest$forest
template$model5.panelar.all$coef[3:9] %>% kable(caption = template$model5.panelar.all$caption)
```

##### Model 6.1

`Case Site    : Individual`\
`Control Site : None`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + nhs111 + ambulance.divert + other.centre + change in ED time`\

```{r template.model6_1, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## template$model6.1.ts.plot
sites <- c('Bishop Auckland',
                  'Hartlepool',
                  'Hemel Hempstead',
                  'Newark',
                  'Rochdale')
## Filter
to.plot <- filter(ed_attendances_by_mode_site_measure_clean,
                  town %in% sites &
                  measure == measure,
                  sub.measure == sub.measure)
## Plot
closed_ts_plot(df            = to.plot,
               sites         = sites,
               indicator     = measure,
               sub.indicator = sub.measure,
               steps         = TRUE,
               lines         = TRUE,
               xaxis.steps   = FALSE,
               join.line     = TRUE,
               legend        = TRUE,
               facet         = TRUE)
template$model6.1.forest$forest
template$model6.1.panelar.all$coef[3:8] %>% kable(caption = template$model6.1.panelar.all$caption)
```

##### Model 6.2

`Case Site    : Individual`\
`Control Site : Primary Matched`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + site + nhs111 + ambulance.divert + other.centre + change in ED time`\

```{r template.model6_2, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## template$model6.2.ts.plot
## Model 6.2
sites <- c('Bishop Auckland', 'Whitehaven',
                   'Hartlepool', 'Grimsby',
                   'Hemel Hempstead', 'Warwick',
                   'Newark', 'Southport',
                   'Rochdale', 'Rotherham')
## Filter
to.plot <- filter(ed_attendances_by_mode_site_measure_clean,
                  town %in% sites &
                  measure == measure,
                  sub.measure == sub.measure)
## Plot
closed_ts_plot(df            = to.plot,
               sites         = sites,
               indicator     = measure,
               sub.indicator = sub.measure,
               steps         = TRUE,
               lines         = TRUE,
               xaxis.steps   = FALSE,
               join.line     = TRUE,
               legend        = TRUE,
               facet         = TRUE)
template$model6.2.forest$forest
template$model6.2.panelar.all$coef[3:8] %>% kable(caption = template$model6.2.panelar.all$caption)
```

##### Model 7



`Case Site    : All`\
`Control Site : Primary Matched`\
`Panel        : LSOA`\
`Model        : observations ~ season + time + closure * site + nhs111 + ambulance.divert + other.centre + change in ED time`\

```{r template.model7, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## template$model7.ts.plot
template$model7.forest$forest
template$model7.panelar.all$coef[3:8] %>% kable(caption = template$model7.panelar.all$caption)
```
