#### Interaction Terms

[R]{https://www.r-project.org/} and [Stata]{https://www.stata.com/} handle interaction terms slightly differently.  The details can be found on the respective help pages ([R interactions]() and [Stata fvvarlist](http://www.stata.com/help.cgi?fvvarlist)).  The following output shows first the results from interacting the two variables `town` and `closure` for Bishop Auckland (where ED closed) v's Whitehaven, and you will see the coefficient for the interaction is `NA` (which is R's internal representation of missing values).

```{r interaction_r1, , echo = TRUE, cache = FALSE, results = 'markup', eval = TRUE}
## Model as called with interaction term between town and closure
mod2 <- c('town * closure', 'season', 'relative.month', 'nhs111', 'other.centre', 'ambulance.divert')
formula.model2 <- reformulate(response   = 'value',
                              termlabels = mod2)
filter(mode.of.arrival.any$model2.df,
       town == 'Bishop Auckland' |
       town == 'Whitehaven') %>%
panelAR(#data            = to.analyse,
        formula         = formula.model2,
        timeVar         = 'relative.month',
        panelVar        = 'town',
        autoCorr        = 'ar1',
        panelCorrMethod = 'pcse')
```

Explicitly deriving a dummy variable which is the product of multiplying the two factor variables (as their numerical representation) gives *exactly* the same results...

```{r interaction_r2, , echo = TRUE, cache = FALSE, results = 'markup', eval = TRUE}
## Derive an independent dummy variable representing the interaction
to.analyse <- filter(mode.of.arrival.any$model2.df,
                     town == 'Bishop Auckland' |
                     town == 'Whitehaven')
to.analyse$town.closure <- as.numeric(to.analyse$town) * as.numeric(to.analyse$closure)
## Redefine the model and run this
formula.model2 <- reformulate(response = 'value',
                              termlabels = c('town', 'closure', 'town.closure', 'season', 'relative.month', 'nhs111', 'other.centre', 'ambulance.divert'))
panelAR(data            = to.analyse,
        formula         = formula.model2,
        timeVar         = 'relative.month',
        panelVar        = 'town'	      ,
        autoCorr        = 'ar1',
        panelCorrMethod = 'pcse')
## Checking the derived variable its clear that the interaction term is colinear
## Cross-tabulate the closure and town.closure to show they are co-linear
table(to.analyse$closure, to.analyse$town.closure)
## List the data to show that they are co-linear
dplyr::select(to.analyse, relative.month, closure, town.closure)

```

Stata is doing very similar in that its deriving a dummy variable for the interaction, setting the reference/baseline group to be that which is the product of the reference/baseline group in the individual components, and then testing for differences between other observed levels, the difference is it doesn't appear to be automatically dropping the term due to colinearity.