---
title: ClosED - Project Advisory Group Meeting 2016-11-30
output:
  html_document:
    theme: sandstone
    toc: false
    toc_float: false
    toc_depth: 5
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
##opts_chunk$set(dev = 'pdf')
opts_chunk$set(cache.path = 'cache/',
               width    = 200,
               fig.height = 18,
               fig.width  = 10)
## Set a seed
set.seed(69027181)
```
# {.tabset}

Model  | Case Site    | Control Site         | Panel | Covariates
-------|--------------|----------------------|-------|----------------------------------------
0      | Individual   | None                 | ED    | `closure`
1      | Individual   | None                 | ED    | `season + time + closure + nhs111 + other.centre + ambulance.diversion`
2      | Individual   | Primary Matched      | ED    | `season + time + closure * site + nhs111 + other.centre + ambulance.diversion`
3      | All          | Primary Matched      | ED    | `season + time + closure * site + nhs111 + other.centre + ambulance.diversion`
4      | Individual   | None                 | LSOA  | `season + time + site + nhs111 + other.centre + ambulance.diversion + change in ED time`
5      | All          | None                 | LSOA  | `season + time + site + nhs111 + other.centre + ambulance.diversion + change in ED time`

## Methods

```{r child = '../hta_report/sections/methods.Rmd', eval = TRUE}
```

## Results {.tabset .tabset-fade}
```{r child = 'results/results.Rmd', eval = TRUE}
```

<!-- ## Validation {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'pag_20161130/validation.Rmd', eval = FALSE}
```
<!-- ## Investigations {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'pag_20161130/investigations.Rmd', eval = FALSE}
```

<!-- ## ToDo {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'pag_20161130/todo.Rmd', eval = FALSE}
```
## References
