Methods are described in detail in the Statistical Analysis Plan which can be viewed [online](https://www.overleaf.com/read/ffzknqdcjkpw).  Once the page has loaded click on PDF at the top of the page to download a PDF copy.

## Software

There are two packages for [R](https://www.r-projects.org/) that implement the Prais-Winsten method of adjusting for auto-correlation in time-series analyses, [panelAR](https://cran.r-project.org/web/packages/panelAR/index.html) or [prais](https://cran.r-project.org/web/packages/prais/index.html).  The intention is to use both to cross-validate the results against each other, however at present time has only permitted one (panelAR) to be implemented.  Further it is intended to cross-validate these against the routines provided in [Stata (v14.1)](https://www.stata.com/) however the constarint of having to work with the data stored on a Virtual Machine (VM) this has not been performed as there may be licensing issues installing a personally licensed version on a multi-user VM environment.

### Models

Five models are tested sequentially with growing complexity and are detailed below.

Model | Case Site  | Control Site     | Panel | Covariates
------|------------|------------------|-------|----------------------------------------
1     | Individual | None             | ED    | season + time + closure + steps
2     | Individual | One Matched      | ED    | season + time + closure * site + steps
3     | Individual | One Matched      | LSOA  | season + time + closure * site + steps + change in ED time
4     | All        | All Controls     | LSOA  | season + time + closure * site + steps + change in ED time
5     | All        | Matched Controls | ED    | season + time + closure * site + steps


#### Model Specifics

Currently panel-corrected standard errors are used which are robust to heteroskedaasticity and contemporaneous correlation across panels, but other options are available, such as a Huber-White style sandwich estimateor for panel heteroskedasticity, panel weighted least squares procedure for heteroskedasticity or Parks-Kmenta FGLS to estimate both heteroskedasticity and correlation.  For full details see [Details under PanelAR](http://www.rdocumentation.org/packages/panelAR/functions/panelAR).

### Panels

The panels that are being considered change depending on the type of anayses that are being performed.  If the summary data across a catchment area is being analysed under the 'step' models then the panels are the hospital/Emergency Departments themselves and no term for differences between the sites can be derived since you can not include a term in the regression equation which is equivalent to the panels themselves.  However, if the data is being considered at the Lower Super Output Area (LSOA) as it is under the 'dose' models then the panels are the LSOAs themselves, since these are the units on which repeated measures over time are available and are being analysed.  This permits the inclusion of a dummy variable for the Emergency Departments

<!--- Run all analyses --->
```{r child = 'subsections/analysis.Rmd', eval = TRUE}
```
<!--- Alternatively load results --->
```{r load_results, eval = FALSE}
## load()
```
