### Bishop Auckland
#### Prais-Winsten Regression
```{r model1-bishop-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.bishop %>% summary()

```
#### Negative-Binomial Time-Series (INGARCH)
```{r model1-bishop-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.bishop.model1 %>% summary()

```

### Hartlepool
#### Prais-Winsten Regression
```{r model1-hartlepool-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.hartlepool %>% summary()

```
#### Negative-Binomial Time-Series (INGARCH)
```{r model1-hartlepool-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.hartlepool.model1 %>% summary()

```

### Hemel Hempstead
#### Prais-Winsten Regression
```{r model1-hemel-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.hartlepool %>% summary()

```
#### Negative-Binomial Time-Series (INGARCH)
```{r model1-hemel-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.hemel.model1 %>% summary()

```


### Newark
#### Prais-Winsten Regression
```{r model1-newark-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.newark %>% summary()

```
#### Negative-Binomial Time-Series (INGARCH)
```{r model1-newark-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.newark.model1 %>% summary()

```

### Rochdale
#### Prais-Winsten Regression
```{r model1-rochdale-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.rochdale %>% summary()

```
#### Negative-Binomial Time-Series (INGARCH)
```{r model1-rochdale-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.rochdale.model1 %>% summary()

```
