### Bishop Auckland
#### Time-Series Plot
```{r model1-bishop-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Bishop Auckland', 'Salford', 'Scarborough', 'Whitehaven'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
filter(mode.of.arrival.ambulance$summary.table.head, town == 'Bishop Auckland')

```

#### Prais-Winsten Regression
```{r model1-bishop-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.bishop %>% summary()

```
#### Negative-Binomial Time-Series
```{r model1-bishop-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.bishop.model1 %>% summary()

```

### Hartlepool
#### Time-Series Plot
```{r model1-hartlepool-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
filter(mode.of.arrival.ambulance$summary.table.head, town == 'Hartlepool')

```

#### Prais-Winsten Regression
```{r model1-hartlepool-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.hartlepool %>% summary()

```
#### Negative-Binomial Time-Series
```{r model1-hartlepool-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.hartlepool.model1 %>% summary()

```

### Hemel Hempstead
#### Time-Series Plot
```{r model1-hemel-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Hemel Hempstead', 'Basingstoke', 'Warwick', 'Yeovil'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
filter(mode.of.arrival.ambulance$summary.table.head, town == 'Hemel Hempstead')


```

#### Prais-Winsten Regression
```{r model1-hemel-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.hemel %>% summary()

```
#### Negative-Binomial Time-Series
```{r model1-hemel-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.hemel.model1 %>% summary()

```


### Newark
#### Time-Series Plot
```{r model1-newark-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Newark', 'Carlisle', 'Salisbury', 'Southport'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
filter(mode.of.arrival.ambulance$summary.table.head, town == 'Newark')

```

#### Prais-Winsten Regression
```{r model1-newark-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.newark %>% summary()

```
#### Negative-Binomial Time-Series
```{r model1-newark-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.newark.model1 %>% summary()

```

### Rochdale
#### Time-Series Plot
```{r model1-rochdale-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Rochdale', 'Rotherham', 'Scunthorpe', 'Wansbeck'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
filter(mode.of.arrival.ambulance$summary.table.head, town == 'Rochdale')

```

#### Prais-Winsten Regression
```{r model1-rochdale-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.rochdale %>% summary()

```
#### Negative-Binomial Time-Series
```{r model1-rochdale-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.rochdale.model1 %>% summary()

```
