```{r extracting_model1, echo = FALSE, cache = FALSE, results = 'hide', message = FALSE, eval = TRUE}
## Model 0
## Extract Negative Binomial Coefficients...
tsglm_coef <- rbind(coef(tsglm.bishop.model1),
                    coef(tsglm.hemel.model1),
                    coef(tsglm.hartlepool.model1),
                    coef(tsglm.newark.model1),
                    coef(tsglm.rochdale.model1)) %>%
              as.data.frame()
tsglm_coef$site <- c('Bishop Auckland', 'Hemel Hempstead', 'Hartlepool', 'Newark', 'Rochdale')
tsglm_coef <- melt(tsglm_coef, id.vars = 'site')
names(tsglm_coef) <- c('site', 'term', 'est_negbin')
## Extract Negative Binomial Standard Errors...
tsglm_se <- rbind(se(tsglm.bishop.model1)$se,
                    se(tsglm.hemel.model1)$se,
                    se(tsglm.hartlepool.model1)$se,
                    se(tsglm.newark.model1)$se,
                    se(tsglm.rochdale.model1)$se) %>%
            as.data.frame()
tsglm_se$site <- c('Bishop Auckland', 'Hemel Hempstead', 'Hartlepool', 'Newark', 'Rochdale')
tsglm_se <- melt(tsglm_se, id.vars = c('site'))
names(tsglm_se) <- c('site', 'term', 'se_negbin')
## Combine Coefficients and Standard Errors...
tsglm_est <- merge(tsglm_coef, tsglm_se, by = c('site', 'term'))
rm(tsglm_coef, tsglm_se)
## Exponentiate to get percentages
tsglm_est <- mutate(tsglm_est,
                    est_negbin_exp     = exp(tsglm_est$est_negbin),
                    est_negbin_percent = -(1 - exp(tsglm_est$est_negbin)) * 100)
## Combine and extract Prais-Winsten Coefficients...
prais_est <- rbind(mode.of.arrival.ambulance$model1.panelar.bishop.coef,
                    mode.of.arrival.ambulance$model1.panelar.hemel.coef,
                    mode.of.arrival.ambulance$model1.panelar.hartlepool.coef,
                    mode.of.arrival.ambulance$model1.panelar.newark.coef,
                    mode.of.arrival.ambulance$model1.panelar.rochdale.coef) %>%
              as.data.frame()
names(prais_est) <- c('est_prais', 'se_prais', 't', 'p', 'term', 'site', 'indicator', 'sub.indicator', 'r2')
prais_est <- dplyr::select(prais_est, site, term, est_prais, se_prais)
## Combine with Negative Binomial estimates
compare_coef <- merge(tsglm_est,
                      prais_est,
                      by = c('site', 'term'),
                      all.x = TRUE)
## Get the Mean in each site before/after, calculate absolute & percentage changed
mean_sd <- dplyr::filter(ed_attendances_by_mode_site_measure_clean,
                         sub.measure == 'ambulance') %>%
           group_by(town, closure) %>%
           summarise(me_an  = mean(value, na.rm = TRUE),
                     s_d   = sd(value, na.rm = TRUE))
names(mean_sd) <- c('site', 'closure', 'me_an', 's_d')
mean_sd
mean_sd <- melt(mean_sd, id.vars = c('site', 'closure')) %>% as.data.frame()
mean_sd <- dcast(mean_sd,
                 site ~ variable + closure)
names(mean_sd) <- c('site', 'mean_before', 'mean_after', 'sd_before', 'sd_after')
mean_sd <- mutate(mean_sd,
                  diff = mean_after - mean_before,
                  diff_perc = 100 * (mean_after - mean_before) / mean_before)
## Combine with model coefficients
compare_coef_model1 <- merge(compare_coef,
                             mean_sd,
                             by = c('site'),
                             all.x = TRUE)
## Generate the percentage change of before that Prais-Winsten is reporting
compare_coef_model1 <- mutate(compare_coef_model1,
                               prais_percent = 100 * (est_prais) / mean_before)

```

### Bishop Auckland
#### Time-Series Plot
```{r model1-bishop-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Bishop Auckland', 'Salford', 'Scarborough', 'Whitehaven'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
## filter(mode.of.arrival.ambulance$summary.table.head, town == 'Bishop Auckland') %>%
##     kable()

```

#### Prais-Winsten Regression
```{r model1-bishop-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.bishop %>% summary()

```
```{r model1-bishop-compare, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
to.table <- dplyr::filter(compare_coef_model1, term == 'closure') %>%
dplyr::select(site, mean_before, mean_after, diff, diff_perc, est_prais, prais_percent, est_negbin_percent)
names(to.table) <- c('Site', 'Pre-Mean', 'Post-Mean', 'Difference', 'Percent', 'Prais-Winsten', 'Prais-Winsten (percent)', 'Negative-Binomial (exponentiated)')
filter(to.table, Site == 'Bishop Auckland') %>%
    kable()

```

#### Negative-Binomial Time-Series
```{r model1-bishop-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.bishop.model1 %>% summary()

## Exponentiated Coefficients...
coef(tsglm.bishop.model1) %>% exp()

```

### Hartlepool
#### Time-Series Plot
```{r model1-hartlepool-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
## filter(mode.of.arrival.ambulance$summary.table.head, town == 'Hartlepool') %>%
##     kable()

```

#### Prais-Winsten Regression
```{r model1-hartlepool-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.hartlepool %>% summary()

```
```{r model1-hartlepool-compare, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
to.table <- dplyr::filter(compare_coef_model1, term == 'closure') %>%
dplyr::select(site, mean_before, mean_after, diff, diff_perc, est_prais, prais_percent, est_negbin_percent)
names(to.table) <- c('Site', 'Pre-Mean', 'Post-Mean', 'Difference', 'Percent', 'Prais-Winsten', 'Prais-Winsten (percent)', 'Negative-Binomial (exponentiated)')
filter(to.table, Site == 'Hartlepool') %>%
    kable()

```

#### Negative-Binomial Time-Series
```{r model1-hartlepool-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.hartlepool.model1 %>% summary()

## Exponentiated Coefficients...
coef(tsglm.bishop.model1) %>% exp()

```

### Hemel Hempstead
#### Time-Series Plot
```{r model1-hemel-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Hemel Hempstead', 'Basingstoke', 'Warwick', 'Yeovil'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
## filter(mode.of.arrival.ambulance$summary.table.head, town == 'Hemel Hempstead') %>%
##     kable()


```

#### Prais-Winsten Regression
```{r model1-hemel-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.hemel %>% summary()

```
```{r model1-hemel-compare, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
to.table <- dplyr::filter(compare_coef_model1, term == 'closure') %>%
dplyr::select(site, mean_before, mean_after, diff, diff_perc, est_prais, prais_percent, est_negbin_percent)
names(to.table) <- c('Site', 'Pre-Mean', 'Post-Mean', 'Difference', 'Percent', 'Prais-Winsten', 'Prais-Winsten (percent)', 'Negative-Binomial (exponentiated)')
filter(to.table, Site == 'Hemel Hempstead') %>%
    kable()

```

#### Negative-Binomial Time-Series
```{r model1-hemel-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.hemel.model1 %>% summary()

## Exponentiated Coefficients...
coef(tsglm.bishop.model1) %>% exp()

```


### Newark
#### Time-Series Plot
```{r model1-newark-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Newark', 'Carlisle', 'Salisbury', 'Southport'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
## filter(mode.of.arrival.ambulance$summary.table.head, town == 'Newark') %>%
##     kable()


```

#### Prais-Winsten Regression
```{r model1-newark-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.newark %>% summary()

```
```{r model1-newark-compare, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
to.table <- dplyr::filter(compare_coef_model1, term == 'closure') %>%
dplyr::select(site, mean_before, mean_after, diff, diff_perc, est_prais, prais_percent, est_negbin_percent)
names(to.table) <- c('Site', 'Pre-Mean', 'Post-Mean', 'Difference', 'Percent', 'Prais-Winsten', 'Prais-Winsten (percent)', 'Negative-Binomial (exponentiated)')
filter(to.table, Site == 'Newark') %>%
    kable()

```

#### Negative-Binomial Time-Series
```{r model1-newark-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.newark.model1 %>% summary()

## Exponentiated Coefficients...
coef(tsglm.bishop.model1) %>% exp()

```

### Rochdale
#### Time-Series Plot
```{r model1-rochdale-plot, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure_clean,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               facet         = FALSE,
               sites         = c('Rochdale', 'Rotherham', 'Scunthorpe', 'Wansbeck'),
               legend        = TRUE,
               tidy          = TRUE,
               colour        = TRUE,
               lines         = FALSE,
               xaxis.steps   = TRUE)
## filter(mode.of.arrival.ambulance$summary.table.head, town == 'Rochdale') %>%
##     kable()

```

#### Prais-Winsten Regression
```{r model1-rochdale-prais, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.rochdale %>% summary()

```
```{r model1-rochdale-compare, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
to.table <- dplyr::filter(compare_coef_model1, term == 'closure') %>%
dplyr::select(site, mean_before, mean_after, diff, diff_perc, est_prais, prais_percent, est_negbin_percent)
names(to.table) <- c('Site', 'Pre-Mean', 'Post-Mean', 'Difference', 'Percent', 'Prais-Winsten', 'Prais-Winsten (percent)', 'Negative-Binomial (exponentiated)')
filter(to.table, Site == 'Rochdale') %>%
    kable()

```

#### Negative-Binomial Time-Series
```{r model1-rochdale-negbin, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
tsglm.rochdale.model1 %>% summary()

## Exponentiated Coefficients...
coef(tsglm.bishop.model1) %>% exp()

```
```{r child = 'negbin_model1_interpretation.Rmd', eval = FALSE}
```

### Comparison
#### Comparison and Interpretation



```{r compare_model1, echo = FALSE, cache = FALSE, results = 'markup', message = FALSE, eval = TRUE}
to.table <- dplyr::filter(compare_coef_model1, term == 'closure') %>%
dplyr::select(site, mean_before, mean_after, diff, diff_perc, est_prais, prais_percent, est_negbin_percent)
names(to.table) <- c('Site', 'Pre-Mean', 'Post-Mean', 'Difference', 'Percent', 'Prais-Winsten', 'Prais-Winsten (percent)', 'Negative-Binomial (exponentiated)')
to.table %>%
    kable()
```
