```{r load_results, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
```

### A & E Attendances  {.tabset .tabset-fade}

#### Any  {.tabset .tabset-fade .tabset-pills}
```{r hartlepool_mode_of_arrival_any_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure,
               indicator     = 'ed attendances',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_mode_of_arrival_any_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model1.panelar.hartlepool %>% summary()

```
##### Model 2
```{r hartlepool_mode_of_arrival_any_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model2.panelar.hartlepool %>% summary()

```
##### Model 3a
```{r hartlepool_mode_of_arrival_any_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model3a.panelar.hartlepool %>% summary()

```
##### Model 3b
```{r hartlepool_mode_of_arrival_any_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_mode_of_arrival_any_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model4.panelar %>% summary()

```
##### Model 5
```{r hartlepool_mode_of_arrival_any_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model5.panelar %>% summary()

```
##### Model 6
```{r hartlepool_mode_of_arrival_any_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model6.panelar.hartlepool %>% summary()

```
##### Model 7
```{r hartlepool_mode_of_arrival_any_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model7.panelar %>% summary()

```

#### Ambulance  {.tabset .tabset-fade .tabset-pills}
```{r hartlepool_mode_of_arrival_ambulance_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_mode_of_arrival_ambulance_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.hartlepool %>% summary()

```
##### Model 2
```{r hartlepool_mode_of_arrival_ambulance_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model2.panelar.hartlepool %>% summary()

```
##### Model 3a
```{r hartlepool_mode_of_arrival_ambulance_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model3a.panelar.hartlepool %>% summary()

```

##### Model 3b
```{r hartlepool_mode_of_arrival_ambulance_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model3b.panelar.hartlepool %>% summary()

```
##### Model 4
```{r hartlepool_mode_of_arrival_ambulance_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model4.panelar %>% summary()

```
##### Model 5
```{r hartlepool_mode_of_arrival_ambulance_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model5.panelar %>% summary()

```
##### Model 6
```{r hartlepool_mode_of_arrival_ambulance_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model6.panelar.hartlepool %>% summary()

```
##### Model 7
```{r hartlepool_mode_of_arrival_ambulance_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model7.panelar %>% summary()

```


#### Other  {.tabset .tabset-fade .tabset-pills}
```{r hartlepool_mode_of_arrival_other_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure,
               indicator     = 'ed attendances',
               sub.indicator = 'other',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_mode_of_arrival_other_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model1.panelar.hartlepool %>% summary()

```
##### Model 2
```{r hartlepool_mode_of_arrival_other_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model2.panelar.hartlepool %>% summary()

```

##### Model 3a
```{r hartlepool_mode_of_arrival_other_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model3a.panelar.hartlepool %>% summary()

```

##### Model 3b
```{r hartlepool_mode_of_arrival_other_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_mode_of_arrival_other_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model4.panelar %>% summary()

```
##### Model 5
```{r hartlepool_mode_of_arrival_other_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model5.panelar %>% summary()

```

##### Model 6
```{r hartlepool_mode_of_arrival_other_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model6.panelar.hartlepool %>% summary()

```

##### Model 7
```{r hartlepool_mode_of_arrival_other_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model7.panelar %>% summary()

```

#### Unnecessary  {.tabset .tabset-fade .tabset-pills}
```{r hartlepool_unnecessary_attendance_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = unnecessary_ed_attendances_site_measure,
               indicator     = 'unnecessary ed attendances',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_unnecessary_attendance_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model1.panelar.hartlepool %>% summary()

```
##### Model 2
```{r hartlepool_unnecessary_attendance_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model2.panelar.hartlepool %>% summary()

```

##### Model 3a
```{r hartlepool_unnecessary_attendance_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model3a.panelar.hartlepool %>% summary()

```

##### Model 3b
```{r hartlepool_unnecessary_attendance_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_unnecessary_attendance_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model4.panelar %>% summary()

```
##### Model 5
```{r hartlepool_unnecessary_attendance_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model5.panelar %>% summary()

```

##### Model 6
```{r hartlepool_unnecessary_attendance_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model6.panelar.hartlepool %>% summary()

```

##### Model 7
```{r hartlepool_unnecessary_attendance_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model7.panelar %>% summary()

```


### Emergency Admissions  {.tabset .tabset-fade .tabset-pills}

#### All {.tabset .tabset-fade}
```{r hartlepool_all_emergency_admissions_any_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'all emergency admissions',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_all_emergency_admissions_any_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model1.panelar.hartlepool %>% summary()

```

##### Model 2
```{r hartlepool_all_emergency_admissions_any_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model2.panelar.hartlepool %>% summary()

```

##### Model 3a
```{r hartlepool_all_emergency_admissions_any_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model3a.panelar.hartlepool %>% summary()

```
##### Model 3b
```{r hartlepool_all_emergency_admissions_any_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_all_emergency_admissions_any_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model4.panelar %>% summary()

```

##### Model 5
```{r hartlepool_all_emergency_admissions_any_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model5.panelar %>% summary()

```

##### Model 6
```{r hartlepool_all_emergency_admissions_any_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model6.panelar.hartlepool %>% summary()

```

##### Model 7
```{r hartlepool_all_emergency_admissions_any_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model7.panelar %>% summary()

```


#### All Avoidable Emergency Admissions {.tabset .tabset-fade}
```{r hartlepool_avoidable_emergency_admissions_any_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'avoidable emergency admissions',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_avoidable_emergency_admissions_any_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model1.panelar.hartlepool %>% summary()

```

##### Model 2
```{r hartlepool_avoidable_emergency_admissions_any_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model2.panelar.hartlepool %>% summary()

```

##### Model 3a
```{r hartlepool_avoidable_emergency_admissions_any_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model3a.panelar.hartlepool %>% summary()

```
##### Model 3b
```{r hartlepool_avoidable_emergency_admissions_any_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_avoidable_emergency_admissions_any_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model4.panelar %>% summary()

```

##### Model 5
```{r hartlepool_avoidable_emergency_admissions_any_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model5.panelar %>% summary()

```

##### Model 6
```{r hartlepool_avoidable_emergency_admissions_any_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model6.panelar.hartlepool %>% summary()

```

##### Model 7
```{r hartlepool_avoidable_emergency_admissions_any_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model7.panelar %>% summary()

```



#### ED Attendances Admitted (All) {.tabset .tabset-fade}
```{r hartlepool_ed_attendances_admitted_all_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_ed_attendances_admitted_all_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.all$model1.panelar.hartlepool %>% summary()

```

##### Model 2
```{r hartlepool_ed_attendances_admitted_all_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.all$model2.panelar.hartlepool %>% summary()

```

##### Model 3a
```{r hartlepool_ed_attendances_admitted_all_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.all$model3a.panelar.hartlepool %>% summary()

```
##### Model 3b
```{r hartlepool_ed_attendances_admitted_all_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.all$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_ed_attendances_admitted_all_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.all$model4.panelar %>% summary()

```

##### Model 5
```{r hartlepool_ed_attendances_admitted_all_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.all$model5.panelar %>% summary()

```

##### Model 6
```{r hartlepool_ed_attendances_admitted_all_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.all$model6.panelar.hartlepool %>% summary()

```

##### Model 7
```{r hartlepool_ed_attendances_admitted_all_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.all$model7.panelar %>% summary()

```


#### ED Attendances Admitted (Admitted) {.tabset .tabset-fade}
```{r hartlepool_ed_attendances_admitted_admitted_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'admitted',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_ed_attendances_admitted_admitted_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model1.panelar.hartlepool %>% summary()

```

##### Model 2
```{r hartlepool_ed_attendances_admitted_admitted_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model2.panelar.hartlepool %>% summary()

```

##### Model 3a
```{r hartlepool_ed_attendances_admitted_admitted_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model3a.panelar.hartlepool %>% summary()

```

##### Model 3b
```{r hartlepool_ed_attendances_admitted_admitted_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_ed_attendances_admitted_admitted_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model4.panelar %>% summary()

```

##### Model 5
```{r hartlepool_ed_attendances_admitted_admitted_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model5.panelar %>% summary()

```

##### Model 6
```{r hartlepool_ed_attendances_admitted_admitted_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model6.panelar.hartlepool %>% summary()

```

##### Model 7
```{r hartlepool_ed_attendances_admitted_admitted_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model7.panelar %>% summary()

```


#### ED Attendances Admitted (Fraction Admitted) {.tabset .tabset-fade}
```{r hartlepool_ed_attendances_admitted_fraction_admitted_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'fraction admitted',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model1.panelar.hartlepool %>% summary()

```

##### Model 2
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model2.panelar.hartlepool %>% summary()

```

##### Model 3a
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model3a.panelar.hartlepool %>% summary()

```
##### Model 3b
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model4.panelar %>% summary()

```

##### Model 5
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model5.panelar %>% summary()

```

##### Model 6
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model6.panelar.hartlepool %>% summary()

```

##### Model 7
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model7.panelar %>% summary()

```


<!-- #### Ambulance Time to Hospital {.tabset .tabset-fade .tabset-pills} -->
<!-- ```{r hartlepool_ambulance_mean_time_scene_to_dest_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- closed_ts_plot(df            = amb_mean_times_site_measure, -->
<!--                indicator     = 'ambulance mean times', -->
<!--                sub.indicator = 'scene_to_dest', -->
<!--                steps         = TRUE, -->
<!--                theme         = theme_bw(), -->
<!--                tidy          = FALSE, -->
<!--                facet         = FALSE, -->
<!--                sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'), -->
<!--                legend        = TRUE) -->
<!-- ``` -->

<!-- ##### Model 1 -->
<!-- ```{r hartlepool_ambulance_mean_time_call_to_dest_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- model1.panelar.hartlepool %>% summary() -->

<!-- ``` -->
<!-- ##### Model 2 -->
<!-- ```{r hartlepool_ambulance_mean_time_call_to_dest_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- model2.panelar.hartlepool %>% summary() -->

<!-- ``` -->


### Case Fatality Ratio {.tabset .tabset-fade .tabset-pills}

#### Any  {.tabset .tabset-fade}
```{r hartlepool_case_fatality_ratio_any_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = case_fatality_site_measure,
               indicator     = 'case fatality ratio',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_case_fatality_ratio_any_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model1.panelar.hartlepool %>% summary()

```
##### Model 2
```{r hartlepool_case_fatality_ratio_any_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model2.panelar.hartlepool %>% summary()

```
##### Model 3a
```{r hartlepool_case_fatality_ratio_any_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model3a.panelar.hartlepool %>% summary()

```

##### Model 3b
```{r hartlepool_case_fatality_ratio_any_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_case_fatality_ratio_any_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model4.panelar %>% summary()

```
##### Model 5
```{r hartlepool_case_fatality_ratio_any_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model5.panelar %>% summary()

```
##### Model 6
```{r hartlepool_case_fatality_ratio_any_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model6.panelar.hartlepool %>% summary()

```
##### Model 7
```{r hartlepool_case_fatality_ratio_any_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model7.panelar %>% summary()

```

#### Acute Heart Failure  {.tabset .tabset-fade}
```{r hartlepool_case_fatality_ratio_acute_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = case_fatality_site_measure,
               indicator     = 'case fatality ratio',
               sub.indicator = 'acute heart failure',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

**NB** Currently get errors trying to run models on this outcome.  Under investigation.

##### Model 1
```{r hartlepool_case_fatality_ratio_acute_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model1.panelar.hartlepool %>% summary()

```
##### Model 2
```{r hartlepool_case_fatality_ratio_acute_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model2.panelar.hartlepool %>% summary()

```
##### Model 3a
```{r hartlepool_case_fatality_ratio_acute_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model3a.panelar.hartlepool %>% summary()

```

##### Model 3b
```{r hartlepool_case_fatality_ratio_acute_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_case_fatality_ratio_acute_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model4.panelar %>% summary()

```
##### Model 5
```{r hartlepool_case_fatality_ratio_acute_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model5.panelar %>% summary()

```
##### Model 6
```{r hartlepool_case_fatality_ratio_acute_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model6.panelar.hartlepool %>% summary()

```
##### Model 7
```{r hartlepool_case_fatality_ratio_acute_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model7.panelar %>% summary()

```


### Ambulance Times {.tabset .tabset-fade .tabset-pills}

#### Call to Destination  {.tabset .tabset-fade}

```{r ambulance_mean_times_call_to_dest_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_mean_times_site_measure,
               indicator     = 'ambulance mean times',
               sub.indicator = 'call_to_dest',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hemel Hempstead', 'Basingstoke', 'Warwick', 'Yeovil'),
               legend        = TRUE)
```

**NB** Currently haven't got all models run so there are no results.  Working on this, tricky due to large amount of missing data, so most sites/models can't run.  Worked around for Project Advisory Group so please refer to `~/knitr/pag_20160704.html` for some results (albeit limited).

##### Model 1
```{r hartlepool_case_fatality_ratio_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model1.panelar.hartlepool %>% summary()

```
##### Model 2
```{r hartlepool_case_fatality_ratio_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model2.panelar.hartlepool %>% summary()

```
##### Model 3a
```{r hartlepool_case_fatality_ratio_model3a, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model3a.panelar.hartlepool %>% summary()

```

##### Model 3b
```{r hartlepool_case_fatality_ratio_model3b, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model3b.panelar.hartlepool %>% summary()

```

##### Model 4
```{r hartlepool_case_fatality_ratio_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model4.panelar %>% summary()

```
##### Model 5
```{r hartlepool_case_fatality_ratio_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model5.panelar %>% summary()

```
##### Model 6
```{r hartlepool_case_fatality_ratio_model6, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model6.panelar.hartlepool %>% summary()

```
##### Model 7
```{r hartlepool_case_fatality_ratio_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model7.panelar %>% summary()

```
