### Summary {.tabset .tabset-fade .tabset-pills}

```{r child = 'subsections/summary.Rmd', eval = TRUE}
```

```{r dummy, eval = FALSE}
```

### Attendance - Any {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/mode_of_arrival_any.Rmd', eval = TRUE}
```

### Attendance - Ambulance {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/mode_of_arrival_ambulance.Rmd', eval = TRUE}
```

### Attendance - Other {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/mode_of_arrival_other.Rmd', eval = TRUE}
```

### Attendance - Unnecessary  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/unnecessary_admissions.Rmd', eval = FALSE}
```

### Admissions - All  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ed_attendances_admitted_all.Rmd', eval = TRUE}
```

### Admissions - Admitted  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ed_attendances_admitted_admitted.Rmd', eval = TRUE}
```

### Admissions - Fraction Admitted  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ed_attendances_admitted_fraction_admitted.Rmd', eval = TRUE}
```


### Length of Stay - Any  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/length_of_stay_any.Rmd', eval = FALSE}
```

### Critical Care - All  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/critical_care_all.Rmd', eval = FALSE}
```

### Critical Care - Critical Care  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/critical_care_critical_care.Rmd', eval = FALSE}
```

### Critical Care - Fraction Critical Care  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/critical_care_fraction_critical_care.Rmd', eval = FALSE}
```
