
```{r load_results, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
```

### A & E Attendances  {.tabset .tabset-fade}

#### Any  {.tabset .tabset-fade .tabset-pills}
```{r hartlepool_mode_of_arrival_any_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure,
               indicator     = 'ed attendances',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_mode_of_arrival_any_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model1.panelar.hartlepool %>% summary()
mode.of.arrival.any$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_mode_of_arrival_any_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model2.panelar.hartlepool %>% summary()
mode.of.arrival.any$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_mode_of_arrival_any_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model3.1.panelar.hartlepool %>% summary()
mode.of.arrival.any$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_mode_of_arrival_any_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model3.2.panelar.hartlepool %>% summary()
mode.of.arrival.any$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_mode_of_arrival_any_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model4.panelar %>% summary()
## mode.of.arrival.any$model4.panelar.hartlepool$residuals %>% plot()
```

##### Model 5
```{r hartlepool_mode_of_arrival_any_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model5.panelar %>% summary()
mode.of.arrival.any$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_mode_of_arrival_any_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model6.1.panelar.hartlepool %>% summary()
mode.of.arrival.any$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_mode_of_arrival_any_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model6.2.panelar.hartlepool %>% summary()
mode.of.arrival.any$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_mode_of_arrival_any_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.any$model7.panelar %>% summary()
mode.of.arrival.any$model7.panelar$residuals %>% plot()
```

#### Ambulance  {.tabset .tabset-fade .tabset-pills}
```{r hartlepool_mode_of_arrival_ambulance_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure,
               indicator     = 'ed attendances',
               sub.indicator = 'ambulance',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_mode_of_arrival_ambulance_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model1.panelar.hartlepool %>% summary()
mode.of.arrival.ambulance$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_mode_of_arrival_ambulance_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model2.panelar.hartlepool %>% summary()
mode.of.arrival.ambulance$model2.panelar.hartlepool$residuals %>% plot()

```

##### Model 3.1
```{r hartlepool_mode_of_arrival_ambulance_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model3.1.panelar.hartlepool %>% summary()
mode.of.arrival.ambulance$model3.1.panelar.hartlepool$residuals %>% plot()

```

##### Model 3.2
```{r hartlepool_mode_of_arrival_ambulance_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model3.2.panelar.hartlepool %>% summary()
mode.of.arrival.ambulance$model3.2.panelar.hartlepool$residuals %>% plot()

```

##### Model 4
```{r hartlepool_mode_of_arrival_ambulance_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model4.panelar %>% summary()
mode.of.arrival.ambulance$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_mode_of_arrival_ambulance_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model5.panelar %>% summary()
mode.of.arrival.ambulance$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_mode_of_arrival_ambulance_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model6.1.panelar.hartlepool %>% summary()
mode.of.arrival.ambulance$model6.1.panelar.hartlepool %>% summary()
```

##### Model 6.2
```{r hartlepool_mode_of_arrival_ambulance_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model6.2.panelar.hartlepool %>% summary()
mode.of.arrival.ambulance$model6.2.panelar.hartlepool %>% summary()
```

##### Model 7
```{r hartlepool_mode_of_arrival_ambulance_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.ambulance$model7.panelar %>% summary()
mode.of.arrival.ambulance$model7.panelar$residuals %>% plot()
```


#### Other  {.tabset .tabset-fade .tabset-pills}
```{r hartlepool_mode_of_arrival_other_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_by_mode_site_measure,
               indicator     = 'ed attendances',
               sub.indicator = 'other',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_mode_of_arrival_other_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model1.panelar.hartlepool %>% summary()
mode.of.arrival.other$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_mode_of_arrival_other_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model2.panelar.hartlepool %>% summary()
mode.of.arrival.other$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_mode_of_arrival_other_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model3.1.panelar.hartlepool %>% summary()
mode.of.arrival.other$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_mode_of_arrival_other_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model3.2.panelar.hartlepool %>% summary()
mode.of.arrival.other$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_mode_of_arrival_other_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model4.panelar %>% summary()
mode.of.arrival.other$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_mode_of_arrival_other_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model5.panelar %>% summary()
mode.of.arrival.other$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_mode_of_arrival_other_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model6.1.panelar.hartlepool %>% summary()
mode.of.arrival.other$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_mode_of_arrival_other_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model6.2.panelar.hartlepool %>% summary()
mode.of.arrival.other$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_mode_of_arrival_other_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
mode.of.arrival.other$model7.panelar %>% summary()
mode.of.arrival.other$model7.panelar$residuals %>% plot()
```

#### Unnecessary  {.tabset .tabset-fade .tabset-pills}
```{r hartlepool_unnecessary_attendance_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = unnecessary_ed_attendances_site_measure,
               indicator     = 'unnecessary ed attendances',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_unnecessary_attendance_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model1.panelar.hartlepool %>% summary()
unnecessary.attendance$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_unnecessary_attendance_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model2.panelar.hartlepool %>% summary()
unnecessary.attendance$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_unnecessary_attendance_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model3.1.panelar.hartlepool %>% summary()
unnecessary.attendance$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_unnecessary_attendance_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model3.2.panelar.hartlepool %>% summary()
unnecessary.attendance$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_unnecessary_attendance_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model4.panelar %>% summary()
unnecessary.attendance$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_unnecessary_attendance_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model5.panelar %>% summary()
unnecessary.attendance$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_unnecessary_attendance_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model6.1.panelar.hartlepool %>% summary()
unnecessary.attendance$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_unnecessary_attendance_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model6.2.panelar.hartlepool %>% summary()
unnecessary.attendance$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_unnecessary_attendance_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
unnecessary.attendance$model7.panelar %>% summary()
## unnecessary.attendance$model7.panelar.hartlepool$residuals %>% plot()
```


### Emergency Admissions  {.tabset .tabset-fade .tabset-pills}

#### All {.tabset .tabset-fade}
```{r hartlepool_all_emergency_admissions_any_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'all emergency admissions',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_all_emergency_admissions_any_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model1.panelar.hartlepool %>% summary()
all.emergency.admissions.all$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_all_emergency_admissions_any_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model2.panelar.hartlepool %>% summary()
all.emergency.admissions.all$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_all_emergency_admissions_any_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model3.1.panelar.hartlepool %>% summary()
all.emergency.admissions.all$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_all_emergency_admissions_any_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model3.2.panelar.hartlepool %>% summary()
all.emergency.admissions.all$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_all_emergency_admissions_any_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model4.panelar %>% summary()
all.emergency.admissions.all$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_all_emergency_admissions_any_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model5.panelar %>% summary()
all.emergency.admissions.all$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_all_emergency_admissions_any_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model6.1.panelar.hartlepool %>% summary()
all.emergency.admissions.all$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_all_emergency_admissions_any_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model6.2.panelar.hartlepool %>% summary()
all.emergency.admissions.all$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_all_emergency_admissions_any_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
all.emergency.admissions.all$model7.panelar %>% summary()
all.emergency.admissions.all$model7.panelar$residuals %>% plot()
```


#### All Avoidable Emergency Admissions {.tabset .tabset-fade}
```{r hartlepool_avoidable_emergency_admissions_any_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = emergency_admissions_site_measure,
               indicator     = 'avoidable emergency admissions',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_avoidable_emergency_admissions_any_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model1.panelar.hartlepool %>% summary()
avoidable.emergency.admissions.any$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_avoidable_emergency_admissions_any_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model2.panelar.hartlepool %>% summary()
avoidable.emergency.admissions.any$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_avoidable_emergency_admissions_any_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model3.1.panelar.hartlepool %>% summary()
avoidable.emergency.admissions.any$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_avoidable_emergency_admissions_any_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model3.2.panelar.hartlepool %>% summary()
avoidable.emergency.admissions.any$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_avoidable_emergency_admissions_any_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model4.panelar %>% summary()
avoidable.emergency.admissions.any$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_avoidable_emergency_admissions_any_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model5.panelar %>% summary()
avoidable.emergency.admissions.any$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_avoidable_emergency_admissions_any_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model6.1.panelar.hartlepool %>% summary()
avoidable.emergency.admissions.any$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_avoidable_emergency_admissions_any_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model6.2.panelar.hartlepool %>% summary()
avoidable.emergency.admissions.any$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_avoidable_emergency_admissions_any_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
avoidable.emergency.admissions.any$model7.panelar %>% summary()
avoidable.emergency.admissions.any$model7.panelar$residuals %>% plot()
```



<!-- #### ED Attendances Admitted (All) {.tabset .tabset-fade} -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- closed_ts_plot(df            = ed_attendances_admitted_site_measure, -->
<!--                indicator     = 'ed attendances admitted', -->
<!--                sub.indicator = 'all', -->
<!--                steps         = TRUE, -->
<!--                theme         = theme_bw(), -->
<!--                tidy          = FALSE, -->
<!--                facet         = FALSE, -->
<!--                sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'), -->
<!--                legend        = TRUE) -->
<!-- ``` -->

<!-- ##### Model 1 -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- ed.attendances.admitted.all$model1.panelar.hartlepool %>% summary() -->
<!-- ed.attendances.admitted.all$model1.panelar.hartlepool$residuals %>% plot() -->
<!-- ``` -->

<!-- ##### Model 2 -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- ed.attendances.admitted.all$model2.panelar.hartlepool %>% summary() -->
<!-- ed.attendances.admitted.all$model2.panelar.hartlepool$residuals %>% plot() -->
<!-- ``` -->

<!-- ##### Model 3.1 -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- ed.attendances.admitted.all$model3.1.panelar.hartlepool %>% summary() -->
<!-- ed.attendances.admitted.all$model3.1.panelar.hartlepool$residuals %>% plot() -->
<!-- ``` -->

<!-- ##### Model 3.2 -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- ed.attendances.admitted.all$model3.2.panelar.hartlepool %>% summary() -->
<!-- ed.attendances.admitted.all$model3.2.panelar.hartlepool$residuals %>% plot() -->
<!-- ``` -->

<!-- ##### Model 4 -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- ed.attendances.admitted.all$model4.panelar %>% summary() -->
<!-- ed.attendances.admitted.all$model4.panelar$residuals %>% plot() -->
<!-- ``` -->

<!-- ##### Model 5 -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- ed.attendances.admitted.all$model5.panelar %>% summary() -->
<!-- ed.attendances.admitted.all$model5.panelar$residuals %>% plot() -->
<!-- ``` -->

<!-- ##### Model 6.1 -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- ed.attendances.admitted.all$model6.1.panelar.hartlepool %>% summary() -->
<!-- ed.attendances.admitted.all$model6.1.panelar.hartlepool$residuals %>% plot() -->
<!-- ``` -->

<!-- ##### Model 6.2 -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- ed.attendances.admitted.all$model6.2.panelar.hartlepool %>% summary() -->
<!-- ed.attendances.admitted.all$model6.2.panelar.hartlepool$residuals %>% plot() -->
<!-- ``` -->

<!-- ##### Model 7 -->
<!-- ```{r hartlepool_ed_attendances_admitted_all_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE} -->
<!-- ed.attendances.admitted.all$model7.panelar %>% summary() -->
<!-- ed.attendances.admitted.all$model7.panelar$residuals %>% plot() -->
<!-- ``` -->


#### ED Attendances Admitted (Admitted) {.tabset .tabset-fade}
```{r hartlepool_ed_attendances_admitted_admitted_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'admitted',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_ed_attendances_admitted_admitted_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model1.panelar.hartlepool %>% summary()
ed.attendances.admitted.admitted$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_ed_attendances_admitted_admitted_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model2.panelar.hartlepool %>% summary()
ed.attendances.admitted.admitted$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_ed_attendances_admitted_admitted_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model3.1.panelar.hartlepool %>% summary()
ed.attendances.admitted.admitted$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_ed_attendances_admitted_admitted_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model3.2.panelar.hartlepool %>% summary()
ed.attendances.admitted.admitted$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_ed_attendances_admitted_admitted_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model4.panelar %>% summary()
ed.attendances.admitted.admitted$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_ed_attendances_admitted_admitted_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model5.panelar %>% summary()
ed.attendances.admitted.admitted$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_ed_attendances_admitted_admitted_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model6.1.panelar.hartlepool %>% summary()
ed.attendances.admitted.admitted$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_ed_attendances_admitted_admitted_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model6.2.panelar.hartlepool %>% summary()
ed.attendances.admitted.admitted$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_ed_attendances_admitted_admitted_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.admitted$model7.panelar %>% summary()
ed.attendances.admitted.admitted$model7.panelar$residuals %>% plot()
```


#### ED Attendances Admitted (Fraction Admitted) {.tabset .tabset-fade}
```{r hartlepool_ed_attendances_admitted_fraction_admitted_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'fraction admitted',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model1.panelar.hartlepool %>% summary()
ed.attendances.admitted.fraction.admitted$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model2.panelar.hartlepool %>% summary()
ed.attendances.admitted.fraction.admitted$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model3.1.panelar.hartlepool %>% summary()
ed.attendances.admitted.fraction.admitted$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model3.2.panelar.hartlepool %>% summary()
ed.attendances.admitted.fraction.admitted$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model4.panelar %>% summary()
## ed.attendances.admitted.fraction.admitted$model4.panelar.hartlepool$residuals %>% plot()
```

##### Model 5
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model5.panelar %>% summary()
ed.attendances.admitted.fraction.admitted$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model6.1.panelar.hartlepool %>% summary()
ed.attendances.admitted.fraction.admitted$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model6.2.panelar.hartlepool %>% summary()
ed.attendances.admitted.fraction.admitted$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_ed_attendances_admitted_fraction_admitted_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ed.attendances.admitted.fraction.admitted$model7.panelar %>% summary()
ed.attendances.admitted.fraction.admitted$model7.panelar$residuals %>% plot()
```


### Case Fatality Ratio {.tabset .tabset-fade .tabset-pills}


#### Any  {.tabset .tabset-fade}
```{r hartlepool_case_fatality_ratio_any_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = case_fatality_site_measure,
               indicator     = 'case fatality ratio',
               sub.indicator = 'any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 1
```{r hartlepool_case_fatality_ratio_any_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model1.panelar.hartlepool %>% summary()
## case.fatality.ratio.any$model1.panelar.hartlepool$residauls %>% plot()
```

##### Model 2
```{r hartlepool_case_fatality_ratio_any_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model2.panelar.hartlepool %>% summary()
## case.fatality.ratio.any$model2.panelar.hartlepool$residauls %>% plot()
```

##### Model 3.1
```{r hartlepool_case_fatality_ratio_any_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model3.1.panelar.hartlepool %>% summary()
## case.fatality.ratio.any$model3.1.panelar.hartlepool$residauls %>% plot()
```

##### Model 3.2
```{r hartlepool_case_fatality_ratio_any_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model3.2.panelar.hartlepool %>% summary()
## case.fatality.ratio.any$model3.2.panelar.hartlepool$residauls %>% plot()
```

##### Model 4
```{r hartlepool_case_fatality_ratio_any_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model4.panelar %>% summary()
## case.fatality.ratio.any$model4.panelar$residauls %>% plot()
```

##### Model 5
```{r hartlepool_case_fatality_ratio_any_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model5.panelar %>% summary()
## case.fatality.ratio.any$model5.panelar$residauls %>% plot()
```

##### Model 6.1
```{r hartlepool_case_fatality_ratio_any_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model6.1.panelar.hartlepool %>% summary()
## case.fatality.ratio.any$model6.1.panelar.hartlepool$residauls %>% plot()
```

##### Model 6.2
```{r hartlepool_case_fatality_ratio_any_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model6.2.panelar.hartlepool %>% summary()
## case.fatality.ratio.any$model6.2.panelar.hartlepool$residauls %>% plot()
```

##### Model 7
```{r hartlepool_case_fatality_ratio_any_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
case.fatality.ratio.any$model7.panelar %>% summary()
## case.fatality.ratio.any$model7.panelar$residauls %>% plot()
```

#### Acute Heart Failure  {.tabset .tabset-fade}
```{r hartlepool_case_fatality_ratio_acute_ts_plot, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
closed_ts_plot(df            = case_fatality_site_measure,
               indicator     = 'case fatality ratio',
               sub.indicator = 'acute heart failure',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

**NB** Currently get errors trying to run models on this outcome.  Under investigation.

##### Model 1
```{r hartlepool_case_fatality_ratio_acute_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model1.panelar.hartlepool %>% summary()
case.fatality.ratio.acute.heart.failure$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_case_fatality_ratio_acute_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model2.panelar.hartlepool %>% summary()
case.fatality.ratio.acute.heart.failure$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_case_fatality_ratio_acute_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model3.1.panelar.hartlepool %>% summary()
case.fatality.ratio.acute.heart.failure$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_case_fatality_ratio_acute_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model3.2.panelar.hartlepool %>% summary()
case.fatality.ratio.acute.heart.failure$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_case_fatality_ratio_acute_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model4.panelar %>% summary()
case.fatality.ratio.acute.heart.failure$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_case_fatality_ratio_acute_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model5.panelar %>% summary()
case.fatality.ratio.acute.heart.failure$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_case_fatality_ratio_acute_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model6.1.panelar.hartlepool %>% summary()
case.fatality.ratio.acute.heart.failure$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_case_fatality_ratio_acute_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model6.2.panelar.hartlepool %>% summary()
case.fatality.ratio.acute.heart.failure$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_case_fatality_ratio_acute_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = FALSE}
case.fatality.ratio.acute.heart.failure$model7.panelar %>% summary()
case.fatality.ratio.acute.heart.failure$model7.panelar$residuals %>% plot()
```


### Ambulance Times {.tabset .tabset-fade .tabset-pills}

**NB** Ambulance Service data is incomplete, only Hartlepool and Grimsby data available so no 'pooled' analyses.

#### Call to Destination  {.tabset .tabset-fade}

```{r ambulance_mean_times_call_to_dest_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_mean_times_site_measure,
               indicator     = 'ambulance mean times',
               sub.indicator = 'call_to_dest',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```


##### Model 1
```{r hartlepool_mean_times_call_to_dest_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model1.panelar.hartlepool %>% summary()
ambulance.mean.times.call.to.dest$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_mean_times_call_to_dest_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model2.panelar.hartlepool %>% summary()
ambulance.mean.times.call.to.dest$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_mean_times_call_to_dest_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model3.1.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.dest$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_mean_times_call_to_dest_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model3.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.dest$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_mean_times_call_to_dest_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model4.panelar %>% summary()
## ambulance.mean.times.call.to.dest$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_mean_times_call_to_dest_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model5.panelar %>% summary()
## ambulance.mean.times.call.to.dest$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_mean_times_call_to_dest_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model6.1.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.dest$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_mean_times_call_to_dest_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model6.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.dest$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_mean_times_call_to_dest_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.dest$model7.panelar %>% summary()
## ambulance.mean.times.call.to.dest$model7.panelar$residuals %>% plot()
```


#### Call to Scene (Any)  {.tabset .tabset-fade}

```{r ambulance_mean_times_call_to_scene_any_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_mean_times_site_measure,
               indicator     = 'ambulance mean times',
               sub.indicator = 'call_to_scene_any',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)

```



##### Model 1
```{r hartlepool_mean_times_call_to_scene_any_model1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.any$model1.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.any$model1.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_mean_times_call_to_scene_any_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.any$model2.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.any$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_mean_times_call_to_scene_any_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.any$model3.1.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.any$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_mean_times_call_to_scene_any_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.any$model3.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.any$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_mean_times_call_to_scene_any_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.any$model4.panelar %>% summary()
## ambulance.mean.times.call.to.scene.any$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_mean_times_call_to_scene_any_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.any$model5.panelar %>% summary()
## ambulance.mean.times.call.to.scene.any$model5.panelar$residuals %>% plot()
```

##### Model 6.1
```{r hartlepool_mean_times_call_to_scene_any_model6_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.any$model6.1.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.any$model6.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_mean_times_call_to_scene_any_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.any$model6.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.any$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_mean_times_call_to_scene_any_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.any$model7.panelar %>% summary()
## ambulance.mean.times.call.to.scene.any$model7.panelar$residuals %>% plot()
```

#### Call to Scene (Conveying)  {.tabset .tabset-fade}

```{r ambulance_mean_times_call_to_scene_conveying_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_mean_times_site_measure,
               indicator     = 'ambulance mean times',
               sub.indicator = 'call_to_scene_conveying',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)

```



##### Model 2
```{r hartlepool_mean_times_call_to_scene_conveying_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.conveying$model2.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.conveying$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_mean_times_call_to_scene_conveying_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.conveying$model2.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.conveying$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_mean_times_call_to_scene_conveying_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.conveying$model3.1.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.conveying$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_mean_times_call_to_scene_conveying_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.conveying$model3.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.conveying$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_mean_times_call_to_scene_conveying_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.conveying$model4.panelar %>% summary()
## ambulance.mean.times.call.to.scene.conveying$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_mean_times_call_to_scene_conveying_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.conveying$model5.panelar %>% summary()
## ambulance.mean.times.call.to.scene.conveying$model5.panelar$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_mean_times_call_to_scene_conveying_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.conveying$model6.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.call.to.scene.conveying$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_mean_times_call_to_scene_conveying_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.call.to.scene.conveying$model7.panelar %>% summary()
## ambulance.mean.times.call.to.scene.conveying$model7.panelar$residuals %>% plot()
```

#### Destination to Clear  {.tabset .tabset-fade}

```{r ambulance_mean_times_dest_to_clear_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_mean_times_site_measure,
               indicator     = 'ambulance mean times',
               sub.indicator = 'dest_to_clear',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```


##### Model 2
```{r hartlepool_mean_times_dest_to_clear_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.dest.to.clear$model2.panelar.hartlepool %>% summary()
## ambulance.mean.times.dest.to.clear$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_mean_times_dest_to_clear_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.dest.to.clear$model2.panelar.hartlepool %>% summary()
## ambulance.mean.times.dest.to.clear$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_mean_times_dest_to_clear_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.dest.to.clear$model3.1.panelar.hartlepool %>% summary()
## ambulance.mean.times.dest.to.clear$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_mean_times_dest_to_clear_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.dest.to.clear$model3.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.dest.to.clear$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_mean_times_dest_to_clear_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.dest.to.clear$model4.panelar %>% summary()
## ambulance.mean.times.dest.to.clear$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_mean_times_dest_to_clear_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.dest.to.clear$model5.panelar %>% summary()
## ambulance.mean.times.dest.to.clear$model5.panelar$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_mean_times_dest_to_clear_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.dest.to.clear$model6.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.dest.to.clear$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_mean_times_dest_to_clear_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.dest.to.clear$model7.panelar %>% summary()
## ambulance.mean.times.dest.to.clear$model7.panelar$residuals %>% plot()
```

#### Scene to Destination  {.tabset .tabset-fade}

```{r ambulance_mean_times_scene_to_dest_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_mean_times_site_measure,
               indicator     = 'ambulance mean times',
               sub.indicator = 'scene_to_dest',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```



##### Model 2
```{r hartlepool_mean_times_scene_to_dest_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.scene.to.dest$model2.panelar.hartlepool %>% summary()
## ambulance.mean.times.scene.to.dest$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_mean_times_scene_to_dest_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.scene.to.dest$model2.panelar.hartlepool %>% summary()
## ambulance.mean.times.scene.to.dest$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_mean_times_scene_to_dest_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.scene.to.dest$model3.1.panelar.hartlepool %>% summary()
## ambulance.mean.times.scene.to.dest$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_mean_times_scene_to_dest_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.scene.to.dest$model3.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.scene.to.dest$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_mean_times_scene_to_dest_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.scene.to.dest$model4.panelar %>% summary()
## ambulance.mean.times.scene.to.dest$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_mean_times_scene_to_dest_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.scene.to.dest$model5.panelar %>% summary()
## ambulance.mean.times.scene.to.dest$model5.panelar$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_mean_times_scene_to_dest_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.scene.to.dest$model6.2.panelar.hartlepool %>% summary()
## ambulance.mean.times.scene.to.dest$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_mean_times_scene_to_dest_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.mean.times.scene.to.dest$model7.panelar %>% summary()
## ambulance.mean.times.scene.to.dest$model7.panelar$residuals %>% plot()
```

### Ambulance Non-Conveyance {.tabset .tabset-fade .tabset-pills}

**NB** Ambulance Service data is incomplete, only Hartlepool and Grimsby data available so no 'pooled' analyses.

#### Green Calls  {.tabset .tabset-fade}

```{r ambulance_non_conveyance_green_call_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_non_conveyance_site_measure,
               indicator     = 'ambulance non-conveyance',
               sub.indicator = 'green calls',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```


##### Model 2
```{r hartlepool_non_conveyance_green_call_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls$model2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_non_conveyance_green_call_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls$model2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_non_conveyance_green_call_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls$model3.1.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_non_conveyance_green_call_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls$model3.2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_non_conveyance_green_call_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls$model4.panelar %>% summary()
## ambulance.non.conveyances.green.calls$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_non_conveyance_green_call_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls$model5.panelar %>% summary()
## ambulance.non.conveyances.green.calls$model5.panelar$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_non_conveyance_green_call_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls$model6.2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_non_conveyance_green_call_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls$model7.panelar %>% summary()
## ambulance.non.conveyances.green.calls$model7.panelar$residuals %>% plot()
```


#### Green Calls Not Conveyed {.tabset .tabset-fade}

```{r ambulance_non_conveyances_green_calls_non_conveyed_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_non_conveyance_site_measure,
               indicator     = 'ambulance non-conveyance',
               sub.indicator = 'not conveyed green calls',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 2
```{r hartlepool_non_conveyances_green_calls_non_conveyed_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls.non.conveyed$model2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls.non.conveyed$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_non_conveyances_green_calls_non_conveyed_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls.non.conveyed$model2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls.non.conveyed$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_non_conveyances_green_calls_non_conveyed_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls.non.conveyed$model3.1.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls.non.conveyed$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_non_conveyances_green_calls_non_conveyed_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls.non.conveyed$model3.2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls.non.conveyed$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_non_conveyances_green_calls_non_conveyed_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls.non.conveyed$model4.panelar %>% summary()
## ambulance.non.conveyances.green.calls.non.conveyed$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_non_conveyances_green_calls_non_conveyed_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls.non.conveyed$model5.panelar %>% summary()
## ambulance.non.conveyances.green.calls.non.conveyed$model5.panelar$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_non_conveyances_green_calls_non_conveyed_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls.non.conveyed$model6.2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.green.calls.non.conveyed$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_non_conveyances_green_calls_non_conveyed_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.green.calls.non.conveyed$model7.panelar %>% summary()
## ambulance.non.conveyances.green.calls.non.conveyed$model7.panelar$residuals %>% plot()
```

#### Fraction Not Conveyed {.tabset .tabset-fade}

```{r ambulance_non_conveyances_fraction_not_conveyed_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_non_conveyance_site_measure,
               indicator     = 'ambulance non-conveyance',
               sub.indicator = 'fraction not conveyed',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```

##### Model 2
```{r hartlepool_non_conveyances_fraction_not_conveyed_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.fraction.not.conveyed$model2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.fraction.not.conveyed$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_non_conveyances_fraction_not_conveyed_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.fraction.not.conveyed$model2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.fraction.not.conveyed$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_non_conveyances_fraction_not_conveyed_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.fraction.not.conveyed$model3.1.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.fraction.not.conveyed$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_non_conveyances_fraction_not_conveyed_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.fraction.not.conveyed$model3.2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.fraction.not.conveyed$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_non_conveyances_fraction_not_conveyed_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.fraction.not.conveyed$model4.panelar %>% summary()
## ambulance.non.conveyances.fraction.not.conveyed$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_non_conveyances_fraction_not_conveyed_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.fraction.not.conveyed$model5.panelar %>% summary()
## ambulance.non.conveyances.fraction.not.conveyed$model5.panelar$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_non_conveyances_fraction_not_conveyed_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.fraction.not.conveyed$model6.2.panelar.hartlepool %>% summary()
## ambulance.non.conveyances.fraction.not.conveyed$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_non_conveyances_fraction_not_conveyed_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.non.conveyances.fraction.not.conveyed$model7.panelar %>% summary()
## ambulance.non.conveyances.fraction.not.conveyed$model7.panelar$residuals %>% plot()
```

### Ambulance Red Calls {.tabset .tabset-fade .tabset-pills}

**NB** Ambulance Service data is incomplete, only Hartlepool and Grimsby data available so no 'pooled' analyses.

#### Hospital Transfers  {.tabset .tabset-fade}

```{r ambulance_red_calls_hospital_transfers_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_red_calls_site_measure,
               indicator     = 'ambulance red calls',
               sub.indicator = 'hospital transfers',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```


##### Model 2
```{r hartlepool_red_calls_hospital_transfers_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.hospital.transfers$model2.panelar.hartlepool %>% summary()
## ambulance.red.calls.hospital.transfers$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_red_calls_hospital_transfers_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.hospital.transfers$model2.panelar.hartlepool %>% summary()
## ambulance.red.calls.hospital.transfers$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_red_calls_hospital_transfers_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.hospital.transfers$model3.1.panelar.hartlepool %>% summary()
## ambulance.red.calls.hospital.transfers$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_red_calls_hospital_transfers_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.hospital.transfers$model3.2.panelar.hartlepool %>% summary()
## ambulance.red.calls.hospital.transfers$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_red_calls_hospital_transfers_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.hospital.transfers$model4.panelar %>% summary()
## ambulance.red.calls.hospital.transfers$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_red_calls_hospital_transfers_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.hospital.transfers$model5.panelar %>% summary()
## ambulance.red.calls.hospital.transfers$model5.panelar$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_red_calls_hospital_transfers_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.hospital.transfers$model6.2.panelar.hartlepool %>% summary()
## ambulance.red.calls.hospital.transfers$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_red_calls_hospital_transfers_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.hospital.transfers$model7.panelar %>% summary()
## ambulance.red.calls.hospital.transfers$model7.panelar$residuals %>% plot()
```

#### Total  {.tabset .tabset-fade}

```{r ambulance_red_calls_total_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = amb_red_calls_site_measure,
               indicator     = 'ambulance red calls',
               sub.indicator = 'total',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'),
               legend        = TRUE)
```


##### Model 2
```{r hartlepool_red_calls_total_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.total$model2.panelar.hartlepool %>% summary()
## ambulance.red.calls.total$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 2
```{r hartlepool_red_calls_total_model2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.total$model2.panelar.hartlepool %>% summary()
## ambulance.red.calls.total$model2.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.1
```{r hartlepool_red_calls_total_model3_1, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.total$model3.1.panelar.hartlepool %>% summary()
## ambulance.red.calls.total$model3.1.panelar.hartlepool$residuals %>% plot()
```

##### Model 3.2
```{r hartlepool_red_calls_total_model3_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.total$model3.2.panelar.hartlepool %>% summary()
## ambulance.red.calls.total$model3.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 4
```{r hartlepool_red_calls_total_model4, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.total$model4.panelar %>% summary()
## ambulance.red.calls.total$model4.panelar$residuals %>% plot()
```

##### Model 5
```{r hartlepool_red_calls_total_model5, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.total$model5.panelar %>% summary()
## ambulance.red.calls.total$model5.panelar$residuals %>% plot()
```

##### Model 6.2
```{r hartlepool_red_calls_total_model6_2, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.total$model6.2.panelar.hartlepool %>% summary()
## ambulance.red.calls.total$model6.2.panelar.hartlepool$residuals %>% plot()
```

##### Model 7
```{r hartlepool_red_calls_total_model7, echo = FALSE, cache = FALSE, results = 'markup',  eval = TRUE}
ambulance.red.calls.total$model7.panelar %>% summary()
## ambulance.red.calls.total$model7.panelar$residuals %>% plot()
```
