### Summary {.tabset .tabset-fade .tabset-pills}

```{r child = 'subsections/summary.Rmd', eval = TRUE}
```

```{r dummy, eval = FALSE}
```

### Attendance - Any {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/mode_of_arrival_any.Rmd', eval = TRUE}
```

### Attendance - Ambulance {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/mode_of_arrival_ambulance.Rmd', eval = TRUE}
```

### Attendance - Other {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/mode_of_arrival_other.Rmd', eval = TRUE}
```

### Attendance - Unnecessary  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/unnecessary_attendance.Rmd', eval = TRUE}
```
### Emergency Admissions - All  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/all_emergency_admissions_all.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Any  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_any.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Acute Mnetal Health Crisis  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_acute_mental_health_crisis.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Angina {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_angina.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Blocked Catheter {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_blocked_catheter.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Cellulitis {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_cellulitis.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - COPD {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_copd.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - DVT {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_dvt.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Epileptic Fit {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_epileptic_fit.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Falls (> 76yrs) {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_falls.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Hypoglycaemia {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_hypoglycaemia.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Minor Head Injuries {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_minor_head_injuries.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Non-Specific Chest Pain {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_non_specific_chest_pain.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Pyrexial Child (<6yrs) {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_pyrexial_child.Rmd', eval = TRUE}
```

### Avoidable Emergency Admissions - Urinary Tract Infection {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/avoidable_emergency_admissions_urinary_tract_infection.Rmd', eval = TRUE}
```

### Attendances Admitted - All  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ed_attendances_admitted_all.Rmd', eval = TRUE}
```

### Attendances Admitted - Admitted  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ed_attendances_admitted_admitted.Rmd', eval = TRUE}
```

### Attendances Admitted - Fraction Admitted  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ed_attendances_admitted_fraction_admitted.Rmd', eval = TRUE}
```

### Critical Care - All  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/critical_care_cips_all.Rmd', eval = TRUE}
```

### Critical Care - Critical  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/critical_care_cips_critical.Rmd', eval = TRUE}
```

### Critical Care - Fraction  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/critical_care_cips_fraction.Rmd', eval = TRUE}
```

### Length of Stay - Mean  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/length_of_stay_mean.Rmd', eval = TRUE}
```

### Length of Stay - Median  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/length_of_stay_median.Rmd', eval = TRUE}
```

### Case Fatality Ratio - Any  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_any.Rmd', eval = TRUE}
```

### Case Fatality Ratio - Acute Heart Failure  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_acute_heart_failure.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Anaphylaxis  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_anaphylaxis.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Asphyxiation  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_asphyxiation.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Asthma  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_asthma.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Cardiac Arrest  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_cardiac_arrest.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Falls  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_falls.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Fractured Neck of Femur  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_fractured_neck_of_femur.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Meningitis  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_meningitis.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Myocardial Infarction  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_myocardial_infarction.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Pregnancy and Birth Related  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_pregnancy_and_birth_related.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Road Traffic Accident  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_road_traffic_accident.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Self Harm  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_self_harm.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Septic Shock  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_septic_shock.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Serious Head Injury  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_serious_head_injury.Rmd', eval = FALSE}
```

### Case Fatality Ratio - Stroke CVA  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/case_fatality_ratio_stroke_cva.Rmd', eval = FALSE}
```

### Ambulance Mean Times - Call to Destianation  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ambulance_mean_times_call_to_dest.Rmd', eval = FALSE}
```

### Ambulance Mean Times - Call to Scene (Any)  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ambulance_mean_times_call_to_scene_any.Rmd', eval = FALSE}
```

### Ambulance Mean Times - Call to Scene (Conveying)  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ambulance_mean_times_call_to_scene_conveying.Rmd', eval = FALSE}
```

### Ambulance Mean Times - Scene to Destination  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ambulance_mean_times_scene_to_destination.Rmd', eval = FALSE}
```

### Ambulance Mean Times - Destimation to Clear  {.tabset .tabset-fade .tabset-pills}
```{r child = 'subsections/ambulance_mean_times_destination_to_clear.Rmd', eval = FALSE}
```
