<!--- Load the results --->
```{r load.results, echo = FALSE, cache = FALSE, results = 'hide', message = FALSE, eval = TRUE}
load(file = '~/work/closed/knitr/data/results.RData')

```

### Attendance
#### Any
```{r child = 'subsections/mode_of_arrival_any.Rmd', eval = TRUE}
```

#### Ambulance
```{r child = 'subsections/mode_of_arrival_ambulance.Rmd', eval = TRUE}
```

#### Other
```{r child = 'subsections/mode_of_arrival_other.Rmd', eval = TRUE}
```

#### Unnecessary
```{r child = 'subsections/unnecessary_attendance.Rmd', eval = TRUE}
```

### Emergency Admissions
#### All
```{r child = 'subsections/all_emergency_admissions_all.Rmd', eval = TRUE}
```

#### Avoidable - Any
```{r child = 'subsections/avoidable_emergency_admissions_any.Rmd', eval = TRUE}
```

#### Avoidable - Non-Specific Chest Pain
```{r child = 'subsections/avoidable_emergency_admissions_non_specific_chest_pain.Rmd', eval = FALSE}
```

### Attendances Admitted
#### Admitted
```{r child = 'subsections/ed_attendances_admitted_admitted.Rmd', eval = TRUE}
```

#### Fraction Admitted
```{r child = 'subsections/ed_attendances_admitted_fraction_admitted.Rmd', eval = TRUE}
```

### Critical Care
#### All
```{r child = 'subsections/critical_care_cips_all.Rmd', eval = TRUE}
```

#### Critical
```{r child = 'subsections/critical_care_cips_critical.Rmd', eval = TRUE}
```

#### Fraction
```{r child = 'subsections/critical_care_cips_fraction.Rmd', eval = TRUE}
```

### Length of Stay
#### Mean
```{r child = 'subsections/length_of_stay_mean.Rmd', eval = TRUE}
```

#### Median
```{r child = 'subsections/length_of_stay_median.Rmd', eval = TRUE}
```

### Case Fatality Ratio

#### Any
```{r child = 'subsections/case_fatality_ratio_any.Rmd', eval = TRUE}
```

#### Acute Heart Failure
```{r child = 'subsections/case_fatality_ratio_acute_heart_failure.Rmd', eval = FALSE}
```

#### Stroke CVA
```{r child = 'subsections/case_fatality_ratio_stroke_cva.Rmd', eval = FALSE}
```

### Ambulance Mean Times
#### Call to Destianation
```{r child = 'subsections/ambulance_mean_times_call_to_dest.Rmd', eval = TRUE}
```

#### Call to Scene (Any)
```{r child = 'subsections/ambulance_mean_times_call_to_scene_any.Rmd', eval = TRUE}
```

#### Call to Scene (Conveying)
```{r child = 'subsections/ambulance_mean_times_call_to_scene_conveying.Rmd', eval = TRUE}
```

#### Scene to Destination
```{r child = 'subsections/ambulance_mean_times_scene_to_dest.Rmd', eval = TRUE}
```

#### Destination to Clear
```{r child = 'subsections/ambulance_mean_times_dest_to_clear.Rmd', eval = TRUE}
```

### Ambulance Non-Conveyance
#### Green Calls
```{r child = 'subsections/ambulance_non_conveyances_green_calls.Rmd', eval = TRUE}
```

#### Green Calls Not Conveyed
```{r child = 'subsections/ambulance_non_conveyances_green_calls_non_conveyed.Rmd', eval = TRUE}
```

#### Fraction Not Conveyed
```{r child = 'subsections/ambulance_non_conveyances_fraction_not_conveyed.Rmd', eval = TRUE}
```

### Ambulance Red Calls
#### Hospital Transfers
```{r child = 'subsections/ambulance_red_calls_hospital_transfers.Rmd', eval = TRUE}
```

#### Total
```{r child = 'subsections/ambulance_red_calls_total.Rmd', eval = TRUE}
```
