---
title: ClosED - Negative Binomial Time-Series v's Prais-Winsten (Mode of Arrival - Ambulance)
output:
  html_document:
    theme: sandstone
    toc: false
    toc_float: false
    toc_depth: 5
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
##opts_chunk$set(dev = 'pdf')
opts_chunk$set(cache.path = 'cache/',
               width    = 200,
               fig.height = 8,
               fig.width  = 8)
## Set a seed
set.seed(69027181)
```


Table: Models tested in ClosED

Model  | Case Site    | Control Site         | Panel | Covariates
-------|--------------|----------------------|-------|----------------------------------------
0      | Individual   | None                 | ED    | closure
0.5    | Individual   | None                 | ED    | closure + time
1      | Individual   | None                 | ED    | season + time + closure + nhs111 + other.centre + ambulance.diversion
2      | Individual   | Primary Matched      | ED    | season + time + closure * site + nhs111 + other.centre + ambulance.diversion
3.1    | Individual   | All Matched          | ED    | season + time + closure * pooled.site + site + nhs111 + other.centre + ambulance.diversion
3.2    | Individual   | All Matched (Pooled) | ED  | season + time + closure * pooled.site + nhs111 + other.centre + ambulance.diversion
4      | All          | Primary Matched      | ED    | season + time + closure * site + nhs111 + other.centre + ambulance.diversion
5      | All          | All Matched          | ED    | season + time + closure * site + nhs111 + other.centre + ambulance.diversion
6.1    | Individual   | None                 | LSOA  | season + time + closure * site + nhs111 + other.centre + ambulance.diversion + change in ED time
6.2    | Individual   | Primary Matched      | LSOA  | season + time + closure * site + nhs111 + other.centre + ambulance.diversion + change in ED time
7      | All          | Primary Matched      | LSOA  | season + time + closure * site + nhs111 + other.centre + ambulance.diversion + change in ED time

# {.tabset}

<!--- Run all analyses --->
```{r child = 'sections/subsections/negbin.Rmd', eval = TRUE}
```

## Model 0 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model0.Rmd', eval = TRUE}
```

## Model 0.5 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model0.5.Rmd', eval = TRUE}
```

## Model 1 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model1.Rmd', eval = TRUE}
```

## Model 2 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model2.Rmd', eval = TRUE}
```

## Model 3.1 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model3.1.Rmd', eval = TRUE}
```

## Model 3.2 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model3.2.Rmd', eval = TRUE}
```

## Model 4 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model4.Rmd', eval = TRUE}
```

## Model 5 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model5.Rmd', eval = TRUE}
```

## Model 6.1 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model6.1.Rmd', eval = TRUE}
```

## Model 6.2 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model6.2.Rmd', eval = TRUE}
```

## Model 7 {.tabset .tabset-fade}
```{r child = 'sections/negbin_arrival_amb_model7.Rmd', eval = TRUE}
```
