#### Time-Series Plots

The number of attendances, by any mode (ambulance or otherwise) are plotted below (prior to the removal of potentially spurious data points).  The first figure shows all case sites for comparison, subsequent plots show a given case with its matched control sites.

##### Case Sites

```{r ed_attendances_admitted_all_time_series_plot_case, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Bishop Auckland', 'Hartlepool', 'Hemel Hempstead', 'Newark', 'Rochdale'))
```

##### Control Sites

```{r ed_attendances_admitted_all_time_series_plot_control, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Salford', 'Scarborough', 'Whitehaven',
                                 'Blackburn', 'Grimsby', 'Wigan',
                                 'Basingstoke', 'Warwick', 'Yeovil',
                                 'Carlisle', 'Salisbury', 'Southport',
                                 'Rotherham', 'Scunthorpe', 'Wansbeck'))
```

##### Bishop Auckland

```{r ed_attendances_admitted_all_time_series_plot_bishop, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Bishop Auckland', 'Salford', 'Scarborough', 'Whitehaven'))
```

##### Hartlepool

```{r ed_attendances_admitted_all_time_series_plot_hartlepool, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hartlepool', 'Blackburn', 'Grimsby', 'Wigan'))
```

##### Hemel Hempstead

```{r ed_attendances_admitted_all_time_series_plot_hemel, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Hemel Hempstead', 'Basingstoke', 'Warwick', 'Yeovil'))
```

##### Newark

```{r ed_attendances_admitted_all_time_series_plot_newark, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Newark', 'Carlisle', 'Salisbury', 'Southport'))
```

##### Rochdale

```{r ed_attendances_admitted_all_time_series_plot_rochdale, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
closed_ts_plot(df            = ed_attendances_admitted_site_measure,
               indicator     = 'ed attendances admitted',
               sub.indicator = 'all',
               steps         = TRUE,
               theme         = theme_bw(),
               tidy          = FALSE,
               facet         = FALSE,
               sites         = c('Rochdale', 'Rotherham', 'Scunthorpe', 'Wansbeck'))
```

#### Model 1
